---
title: "Implementation Study Analysis"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    theme: journal
---

# Background

The overall goal of this project is to reduce morbidity and mortality of sick children attending primary care facilities while supporting the rational and efficient use of diagnostics and medicines by healthcare providers. This study is focused on understanding the operational feasibility of multimodal pulse ox use in standard care. The results presented in this document describe several weeks of use of the Masimo pulse oximeter in primary care settings.

```{r setup, include=FALSE}
rm(list=ls())

knitr::opts_chunk$set(echo = FALSE)

# install these packages if not already on your computer
library(plyr)
library(dplyr)
library(tableone)
library(kableExtra)
library(epiDisplay)
library(Hmisc)
library(consort)
library(highcharter)


# Read in (cleaned) data
# Create a text file from within R with the name ".Renviron", then define the variables as below
# filename = "<current-file-name>.csv"
# COUNTRY = "<your-country>"
# After adding the file and content restart R session and you are good to go
# The Renviron will be ignored when pushing changes to Github

#df_og <- read.csv("C:/Users/user/Dropbox/Mon PC (DESKTOP-OMJATUN)/Documents/GitHub/timci-implementation/implementation-data_clean_2024-03-12.csv")
df_og <- read.csv(Sys.getenv("filename"))

# Basic data cleaning/formatting -- do this before subset so all levels are present

## Relationship of caregiver to child 
df_og$cg_relationship <- factor(df_og$cg_relationship,
                                  levels = c("Mother only", "Father only", "Mother and father", "Mother and grandmother", "Grandmother only", "Grandfather only","Sibling", "Other family member", "Community member"))

## Convert categorical variables into factors
df_og$age_cat <- factor(df_og$age_cat, labels=c("0-1 month", "2-59 months"))
df_og$cg_age_cat <- factor(df_og$cg_age_cat, labels = c("18-21 years", "22-25 years", "26-29 years", "30-34 years", "35-40 years", "41-80 years"))
df_og$household_children_cat <- factor(df_og$household_children_cat, labels = c("0-1", "2-3", "4-5", "6+"))

## Factor clinical variables
df_og$weight_yn <- factor(df_og$weight_yn, levels = c(0,1,2), labels = c("Unknown/not recorded", "Yes", "Recorded, not readable"))
df_og$height_yn <- factor(df_og$height_yn, levels = c(0,1), labels = c("Unknown/not recorded", "Yes"))
df_og$muac_yn <- factor(df_og$muac_yn, levels = c(0,1,2), labels = c("Unknown/not recorded", "Yes", "Recorded, not readable"))
df_og$wfh_yn <- factor(df_og$wfh_yn, levels = c(0,1), labels = c("Unknown/not recorded", "Yes"))
df_og$temp_yn <- factor(df_og$temp_yn, levels = c(0,1), labels = c("Unknown/not recorded", "Yes"))
df_og$hb_yn <- factor(df_og$hb_yn, levels = c(0,1,2), labels = c("Unknown/not recorded", "Yes", "Recorded, not readable"))
df_og$cough_dyspnea_assessed <- factor(df_og$cough_dyspnea_assessed, levels = c("Cough or dyspnea assessed", "Neither assessed"))

## Factor pulse ox variables
df_og$correct_use_yn <- factor(df_og$correct_use_yn, levels = c(0,1,2), labels = c("No", "Yes", "Yes for some measurements but not all"))
df_og$used_po_yn <- factor(df_og$used_po_yn, levels = c(0,1), labels = c("No", "Yes"))
df_og$clinical_measures_complete <- factor(df_og$clinical_measures_complete, levels = c(0,1), labels = c("No", "Yes"))

## Factor dx variables
df_og$cough_dx <- factor(df_og$cough_dx, levels = c(0,1,2), labels = c("Green", "Yellow", "Red"))
df_og$diarrhea_dx <- factor(df_og$diarrhea_dx, levels = c(0,1,2), labels = c("Green", "Yellow", "Red"))
df_og$fever_dx <- factor(df_og$fever_dx, levels = c(0,1,2), labels = c("Green", "Yellow", "Red"))
df_og$ear_dx <- factor(df_og$ear_dx, levels = c(0,1,2), labels = c("Green", "Yellow", "Red"))
df_og$malnutrition_dx <- factor(df_og$malnutrition_dx, levels = c(0,1,2), labels = c("Green", "Yellow", "Red"))
df_og$anemia_dx <- factor(df_og$anemia_dx, levels = c(0,1,2), labels = c("Green", "Yellow", "Red"))
df_og$hiv_dx <- factor(df_og$hiv_dx, levels = c(0,1,2), labels = c("Green", "Yellow", "Red"))

## Travel variables
df_og$travel_mode <- factor(df_og$travel_mode, 
                                  levels = c("Bicycle/Motorcycle","Bicycle/Motorcycle & Bus", "Bicycle/Motorcycle & Walk", "Bicycle/Motorcycle & Car", "Car & Walk", "Other", "Private or Shared car", "Public mini-van/bus", "Public or Private taxi",  "Taxi & Bicycle/Motorcycle", "Taxi & Walk", "Walk", "Walk & Bus"))
df_og$travel_time <- factor(df_og$travel_time, levels= c(1,2,3,4),
                                    labels = c("<30 minutes", "30-60 minutes", "60-120 minutes", ">120 minutes"))
# df_og$travel_cost <- factor(df_og$travel_cost, labels = c("0", "1-20 KSH","21-40 KSH", "41-60 KSH", "61-80 KSH","81-100 KSH",">100 KSH","1-1000 TSH", "1001-5000 TSH", "5001-10000 TSH", ">10000 TSH", "<500 CFA", "500-999 CFA", "1000-3000 CFA", ">3000 CFA"))

## Referral and abx
df_og$referral2 <- factor(df_og$referral, levels = c(1,2,5), labels = c("Urgent", "Non-urgent", "Recorded as not referred"))
df_og$referral <- factor(df_og$referral, levels = c(1,2,4,5), labels = c("Urgent", "Non-urgent", "Recorded, not readable","Recorded as not referred"))
df_og$abx_yn <- factor(df_og$abx_yn, levels = c(0,1), labels = c("No", "Yes"))
                            
## Sex - omitted since data collected on 'sex' was that of the providers and not the caregiver/child

## Maternal education
df_og$cg_edu_mother<- factor(df_og$cg_edu_mother,levels = c(1,2,3,4,5,6,7,8),
                              labels = c("Primary", "Post-primary/vocational", "Secondary", "Diploma/certificate", "Bachelors degree or equivalent", "Masters degree or equivalent", "Other", "Never attended any formal schooling"))

## Household head
df_og$household_head<- factor(df_og$household_head,levels = c(1,2,3,4,5,6,7,8,9,10),
                               labels = c("Female", "Mother of sick child", "Grandmother (maternal)", "Grandmother (paternal)", "Other female", "Male", "Father of sick child", "Grandfather (maternal)", "Grandfather (paternal)", "Other male"))

## Household toilet
df_og$household_toilet<- factor(df_og$household_toilet,levels = c(1,2,3,4,5,6,7,8,9),
                                 labels = c("Flush or pour-flush toilet", "Ventilated improved pit latrine", "Pit latrine with slab", "Pit latrine without slab/open pit", "Composting toilet", "Bucket", "Hanging toilet", "No facility/bush", "Other"))

## Household fuel
df_og$household_fuel<- factor(df_og$household_fuel,levels = c(1,2,3,4,5,6,7),
                               labels = c("Firewood", "Charcoal", "Solar", "Biomass fuel", "Cooking gas (LPG fuel)", "Electricity", "Other"))

## Household water located in house
df_og$household_water_loc<- factor(df_og$household_water_loc, levels= c(1,2),
                                    labels = c("In the house/grounds", "Outside the grounds"))

## Household water time
df_og$household_water_time<- factor(df_og$household_water_time, levels= c(1,2,3,4,5),
                                    labels = c("<5 minutes", "5-15 minutes", "15-30 minutes", "30-60 minutes", ">60 minutes"))

## Household floor
df_og$household_floor <- factor(df_og$household_floor, 
                                 levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20),
                                 labels = c("Natural", "Earth", "Sand", "Clay", "Mud", "Dung", "Rudimentary", "Tablets/Wood planks",
                                            "Palm", "Bamboo", "Mat", "Adobe", "Finished", "Parquet", "Vinyl", "Linoleum", "Ceramic,tile",
                                            "Carpet", "Stone, cement", "Bricks"))

# Create any other sxs red variable for use in indicator three
df_og$any_other_red <- ifelse(df_og$cough_dx=="Red" | df_og$fever_dx=="Red" | df_og$ear_dx=="Red" | df_og$malnutrition_dx=="Red" | df_og$anemia_dx=="Red" | df_og$hiv_dx=="Red", 1, 0)

# Define country and subset
#COUNTRY <- Sys.getenv("COUNTRY")
df_sn <- subset(df_og, df_og$country=="Senegal")
df_sn_cat1 <- subset(df_sn, age_cat=="0-1 month")
df_sn_cat2 <- subset(df_sn, age_cat=="2-59 months")
df_tz <- subset(df_og, df_og$country=="Tanzania")
df_tz_cat1 <- subset(df_tz, age_cat=="0-1 month")
df_tz_cat2 <- subset(df_tz, age_cat=="2-59 months")
df_ka <- subset(df_og, df_og$country=="Kenya")
df_ka_cat1 <- subset(df_ka, age_cat=="0-1 month")
df_ka_cat2 <- subset(df_ka, age_cat=="2-59 months")
```

```{r}
# Add highchart theme
plosgph_theme <- hc_theme(chart = list(
                            style = list(fontFamily = "Arial, sans-serif")
                                  ))
```


# Table 1: Patient demographic and household characteristics. {.tabset}

## Senegal
```{r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("shared_toilet_yn")

# Specify all the variables to include
myVars <- c("age_cat", "cg_relationship", "cg_age_cat", "cg_edu_mother", "household_head", "household_children_cat", "household_toilet", "shared_toilet_yn", "household_fuel", "household_water_loc", "household_water_time", "household_floor")

# CreateTableOne:
out1 <- CreateTableOne(vars = myVars,
                       data = df_sn,
                       factorVars = factorVars,
                       strata = "facility_name",
                       test = FALSE,
                       addOverall = TRUE) 

t1_overall <- print(out1,
            cramVars = c("household_water_loc"))

# Create row labels
t1lab <- c("N",
           "Age Category: 2-59 months (%)",
            "Caregiver Relationship (%)", "Mother only","Father only","Mother and father","Mother and grandmother","Grandmother only","Grandfather only","Sibling","Other family member", "Community member", 
           "Caregiver Age (%)", "18-21 years", "22-25 years", "26-29 years", "30-34 years", "35-40 years", "41-80 years",
            "Maternal Education (highest level attended) (%)", "Primary", "Post-Primary/Vocational", "Secondary", "Diploma/Certificate", "Bachelors degree or equivalent", "Masters degree or equivalent", 
              "Other", "Never attended any formal schooling", 
            "Household head (%)", "Female", "Mother of sick child", "Grandmother (maternal)", "Grandmother (paternal)", "Other female", "Male", "Father of sick child", "Grandfather (maternal)", "Grandfather (paternal)", "Other male", 
           "Number of children under 5y living in household (%)", "0-1", "2-3", "4-5", "6+",
            "What kind of toilet facility do members of your household usually use? (%)", "Flush or pour-flush toilet", "Ventilated improved pit latrine", "Pit latrine with slab", "Pit latrine without slab/open pit", "Composting toilet", "Bucket", "Hanging toilet", "No facility/bush", "Other",
           "Household toilet shared w/another household (%)",
            "What type of fuel is mainly used for cooking in the household? (%)", "Firewood","Charcoal", "Solar",  "Biomass fuel", "Cooking gas (LPG fuel)", "Electricity", "Other",
            "Household water location = In the house or grounds/ Outside the grounds (%)",
           "Time taken to get to main water source (%)", "<5 minutes", "5-15 minutes", "15-30 minutes", "30-60 minutes", ">60 minutes",
            "What is the main material of the floor of the household? (%)", "Natural", "Earth", "Sand", "Clay", "Mud", "Dung", "Rudimentary", "Tablets/Wood planks", "Palm", "Bamboo", "Mat", "Adobe", "Finished", "Parquet", "Vinyl", "Linoleum", "Ceramic,tile", "Carpet", "Stone, cement", "Bricks")


# Add row labels
rownames(t1_overall) <- c(t1lab)

# Table formatting
t1_sn <- kable(t1_overall, col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center")  %>%
  add_indent(c(4:12, 14:19, 21:28, 30:39, 41:44, 46:54, 57:63, 66:70, 72:91)) %>%
  pack_rows("Demographic Characteristics", 2, 28) %>%
  pack_rows("Household Characteristics", 29, 91)
```
`r t1_sn`

## Tanzania
```{r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("shared_toilet_yn")

# Specify all the variables to include
myVars <- c("age_cat", "cg_relationship", "cg_age_cat", "cg_edu_mother", "household_head", "household_children_cat", "household_toilet", "shared_toilet_yn", "household_fuel", "household_water_loc", "household_water_time", "household_floor")

# CreateTableOne:
out1 <- CreateTableOne(vars = myVars,
                       data = df_tz,
                       factorVars = factorVars,
                       strata = "facility_name",
                       test = FALSE,
                       addOverall = TRUE) 

t1_overall <- print(out1,
            cramVars = c("household_water_loc"))

# Create row labels
t1lab <- c("N",
           "Age Category: 2-59 months (%)",
            "Caregiver Relationship (%)", "Mother only","Father only","Mother and father","Mother and grandmother","Grandmother only","Grandfather only","Sibling","Other family member", "Community member",  
           "Caregiver Age (%)", "18-21 years", "22-25 years", "26-29 years", "30-34 years", "35-40 years", "41-80 years",
            "Maternal Education (highest level attended) (%)", "Primary", "Post-Primary/Vocational", "Secondary", "Diploma/Certificate", "Bachelors degree or equivalent", "Masters degree or equivalent", 
              "Other", "Never attended any formal schooling", 
            "Household head (%)", "Female", "Mother of sick child", "Grandmother (maternal)", "Grandmother (paternal)", "Other female", "Male", "Father of sick child", "Grandfather (maternal)", "Grandfather (paternal)", "Other male", 
           "Number of children under 5y living in household (%)", "0-1", "2-3", "4-5", "6+",
            "What kind of toilet facility do members of your household usually use? (%)", "Flush or pour-flush toilet", "Ventilated improved pit latrine", "Pit latrine with slab", "Pit latrine without slab/open pit", "Composting toilet", "Bucket", "Hanging toilet", "No facility/bush", "Other",
           "Household toilet shared w/another household (%)",
            "What type of fuel is mainly used for cooking in the household? (%)", "Firewood","Charcoal", "Solar",  "Biomass fuel", "Cooking gas (LPG fuel)", "Electricity", "Other",
            "Household water location = In the house or grounds/ Outside the grounds (%)",
           "Time taken to get to main water source (%)", "<5 minutes", "5-15 minutes", "15-30 minutes", "30-60 minutes", ">60 minutes",
            "What is the main material of the floor of the household? (%)", "Natural", "Earth", "Sand", "Clay", "Mud", "Dung", "Rudimentary", "Tablets/Wood planks", "Palm", "Bamboo", "Mat", "Adobe", "Finished", "Parquet", "Vinyl", "Linoleum", "Ceramic,tile", "Carpet", "Stone, cement", "Bricks")


# Add row labels
rownames(t1_overall) <- c(t1lab)

# Table formatting
t1_tz <- kable(t1_overall, col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center")  %>%
  add_indent(c(4:12, 14:19, 21:28, 30:39, 41:44, 46:54, 57:63, 66:70, 72:91)) %>%
  pack_rows("Demographic Characteristics", 2, 28) %>%
  pack_rows("Household Characteristics", 29, 91)
```
`r t1_tz`

## Kenya
```{r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("shared_toilet_yn")

# Specify all the variables to include
myVars <- c("age_cat", "cg_relationship", "cg_age_cat", "cg_edu_mother", "household_head", "household_children_cat", "household_toilet", "shared_toilet_yn", "household_fuel", "household_water_loc", "household_water_time", "household_floor")

# CreateTableOne:
out1 <- CreateTableOne(vars = myVars,
                       data = df_ka,
                       factorVars = factorVars,
                       strata = "facility_name",
                       test = FALSE,
                       addOverall = TRUE) 

t1_overall <- print(out1,
            cramVars = c("household_water_loc"))

# Create row labels
t1lab <- c("N",
           "Age Category: 2-59 months (%)",
            "Caregiver Relationship (%)", "Mother only","Father only","Mother and father","Mother and grandmother","Grandmother only","Grandfather only","Sibling","Other family member", "Community member",  
           "Caregiver Age (%)", "18-21 years", "22-25 years", "26-29 years", "30-34 years", "35-40 years", "41-80 years",
            "Maternal Education (highest level attended) (%)", "Primary", "Post-Primary/Vocational", "Secondary", "Diploma/Certificate", "Bachelors degree or equivalent", "Masters degree or equivalent", 
              "Other", "Never attended any formal schooling", 
            "Household head (%)", "Female", "Mother of sick child", "Grandmother (maternal)", "Grandmother (paternal)", "Other female", "Male", "Father of sick child", "Grandfather (maternal)", "Grandfather (paternal)", "Other male", 
           "Number of children under 5y living in household (%)", "0-1", "2-3", "4-5", "6+",
            "What kind of toilet facility do members of your household usually use? (%)", "Flush or pour-flush toilet", "Ventilated improved pit latrine", "Pit latrine with slab", "Pit latrine without slab/open pit", "Composting toilet", "Bucket", "Hanging toilet", "No facility/bush", "Other",
           "Household toilet shared w/another household (%)",
            "What type of fuel is mainly used for cooking in the household? (%)", "Firewood","Charcoal", "Solar",  "Biomass fuel", "Cooking gas (LPG fuel)", "Electricity", "Other",
            "Household water location = In the house or grounds/ Outside the grounds (%)",
           "Time taken to get to main water source (%)", "<5 minutes", "5-15 minutes", "15-30 minutes", "30-60 minutes", ">60 minutes",
            "What is the main material of the floor of the household? (%)", "Natural", "Earth", "Sand", "Clay", "Mud", "Dung", "Rudimentary", "Tablets/Wood planks", "Palm", "Bamboo", "Mat", "Adobe", "Finished", "Parquet", "Vinyl", "Linoleum", "Ceramic,tile", "Carpet", "Stone, cement", "Bricks")


# Add row labels
rownames(t1_overall) <- c(t1lab)

# Table formatting
t1_ka <- kable(t1_overall, col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center")  %>%
  add_indent(c(4:12, 14:19, 21:28, 30:39, 41:44, 46:54, 57:63, 66:70, 72:91)) %>%
  pack_rows("Demographic Characteristics", 2, 28) %>%
  pack_rows("Household Characteristics", 29, 91)
```
`r t1_ka`

# Table 2: Patient clinical and care seeking characteristics. {.tabset}

## Senegal
```{r include=FALSE}
df_sn$travel_cost <- factor(df_sn$travel_cost, levels = c("<500 CFA", "500-999 CFA", "1000-3000 CFA", ">3000 CFA"))

# Specify all the variables you want to treat as factors
factorVars <- c("visit_rsn_illness", "cg_report_cough", "cg_report_rapidbreathing", "cg_report_fever", "cg_report_diarrhea", "cg_report_vomit", "cg_report_other", "medical_hx___1", "medical_hx___2", "medical_hx___6", "medical_hx___7", "medical_hx___9", "medical_hx___10", "medical_hx___11", "medical_hx___12", "medical_hx___13")

# Specify all the variables to include
myVars <- c("visit_rsn_illness", "cg_report_cough", "cg_report_rapidbreathing", "cg_report_fever", "cg_report_diarrhea", "cg_report_vomit", "cg_report_other", "care_locations_num", "travel_mode", "travel_time", "travel_cost",  "medical_hx___1", "medical_hx___2", "medical_hx___6", "medical_hx___7",  "medical_hx___9", "medical_hx___10", "medical_hx___11", "medical_hx___12", "medical_hx___13")

# CreateTableOne:
out2 <- CreateTableOne(vars = myVars,
                       data = df_sn,
                       factorVars = factorVars,
                       strata = "facility_name",
                       test = FALSE,
                       addOverall = TRUE) 

t2_overall <- print(out2)

# Create row labels
t2lab <- c("N", "Visit reason illness (%)",
           "Cough", "Rapid breathing", "Fever", "Diarrhea", "Vomiting", "Other",
           "Number of locations visited for this illness (mean (SD))",
            "Travel mode", "Bicycle/Motorcycle", "Bicycle/Motorcycle & Bus", "Bicycle/Motorcycle & Walk", "Bicycle/Motorcycle & Car", "Car & Walk", "Other", "Private or Shared car", "Public mini-van/bus", 
                "Public or private taxi", "Taxi & Bicycle/Motorcycle", "Taxi & Walk", "Walk", "Walk & Bus",
            "Travel time to arrive at clinic ", "<30 minutes", "30-60 minutes", "1-2 hours", ">2 hours",
            "Estimated amount of money spent for transport to arrive at clinic", "<500 CFA", "500-999 CFA", "1000-3000 CFA", ">3000 CFA",
            "Asthma", "Chicken pox", "Diptheria", "Jaundice", "Malnutrition", "Pneumonia", "TB", "Diarrhea", "Malaria")


# Add row labels
rownames(t2_overall) <- c(t2lab)

# Table formatting
t2_sn <- kable(t2_overall, col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center") %>%
  add_indent(c(11:23, 25:28, 30:33)) %>%
  pack_rows("Symptoms reported by caregiver (%)", 3, 8) %>%
  pack_rows("Travel to clinic (%)", 9, 33) %>%
  pack_rows("Medical history (%)", 34, 42)
```
`r t2_sn`

## Tanzania
```{r include=FALSE}
df_tz$travel_cost <- factor(df_tz$travel_cost, levels = c("0", "1-1000 TSH", "1001-5000 TSH", "5001-10000 TSH", ">10000 TSH"))

# Specify all the variables you want to treat as factors
factorVars <- c("visit_rsn_illness", "visit_rsn_trauma", "visit_rsn_routine", "cg_report_cough", "cg_report_rapidbreathing", "cg_report_fever", "cg_report_diarrhea", "cg_report_vomit", "cg_report_other", "medical_hx___1", "medical_hx___9", "medical_hx___10", "medical_hx___12", "medical_hx___13")

# Specify all the variables to include
myVars <- c("visit_rsn_illness", "visit_rsn_trauma", "visit_rsn_routine", "cg_report_cough", "cg_report_rapidbreathing", "cg_report_fever", "cg_report_diarrhea", "cg_report_vomit", "cg_report_other", "care_locations_num", "travel_mode", "travel_time", "travel_cost",  "medical_hx___1", "medical_hx___9", "medical_hx___10", "medical_hx___12", "medical_hx___13")

# CreateTableOne:
out2 <- CreateTableOne(vars = myVars,
                       data = df_tz,
                       factorVars = factorVars,
                       strata = "facility_name",
                       test = FALSE,
                       addOverall = TRUE) 

t2_overall <- print(out2)

# Create row labels
t2lab <- c("N", "Illness", "Trauma", "Routine",
           "Cough", "Rapid breathing", "Fever", "Diarrhea", "Vomiting", "Other",
           "Number of locations visited for this illness (mean (SD))",
            "Travel mode", "Bicycle/Motorcycle", "Bicycle/Motorcycle & Bus", "Bicycle/Motorcycle & Walk", "Bicycle/Motorcycle & Car", "Car & Walk", "Other", "Private or Shared car", "Public mini-van/bus", 
                "Public or private taxi", "Taxi & Bicycle/Motorcycle", "Taxi & Walk", "Walk", "Walk & Bus",
            "Travel time to arrive at clinic", "<30 minutes", "30-60 minutes", "1-2 hours", ">2 hours",
            "Estimated amount of money spent for transport to arrive at clinic", "0 TSH", "1-1000 TSH", "1001-5000 TSH", "5001-10000 TSH", ">10000 TSH",
            "Asthma", "Malnutrition", "Pneumonia", "Diarrhea", "Malaria")


# Add row labels
rownames(t2_overall) <- c(t2lab)

# Table formatting
t2_tz <- kable(t2_overall, col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center") %>%
  add_indent(c(13:25, 27:30, 32:36)) %>%
  pack_rows("Visit reason (%)", 2, 4) %>%
  pack_rows("Symptoms reported by caregiver (%)", 5, 10) %>%
  pack_rows("Travel to clinic (%)", 11, 36) %>%
  pack_rows("Medical history (%)", 37, 41)
```
`r t2_tz`

## Kenya
```{r include=FALSE}
df_ka$travel_cost <- factor(df_ka$travel_cost, levels = c("0", "1-20 KSH", "21-40 KSH", "41-60 KSH", "61-80 KSH", "81-100 KSH", ">100 KSH"))

# Specify all the variables you want to treat as factors
factorVars <- c("visit_rsn_illness", "visit_rsn_trauma", "visit_rsn_immunize", "visit_rsn_routine", "cg_report_cough", "cg_report_rapidbreathing", "cg_report_fever", "cg_report_diarrhea", "cg_report_vomit", "cg_report_other", "medical_hx___1", "medical_hx___7", "medical_hx___8", "medical_hx___9", "medical_hx___10", "medical_hx___12", "medical_hx___13", "medical_hx___14")

# Specify all the variables to include
myVars <- c("visit_rsn_illness", "visit_rsn_trauma", "visit_rsn_immunize", "visit_rsn_routine", "cg_report_cough", "cg_report_rapidbreathing", "cg_report_fever", "cg_report_diarrhea", "cg_report_vomit", "cg_report_other", "care_locations_num", "travel_mode", "travel_time", "travel_cost",  "medical_hx___1", "medical_hx___7", "medical_hx___8", "medical_hx___9", "medical_hx___10", "medical_hx___12", "medical_hx___13", "medical_hx___14")

# CreateTableOne:
out2 <- CreateTableOne(vars = myVars,
                       data = df_ka,
                       factorVars = factorVars,
                       strata = "facility_name",
                       test = FALSE,
                       addOverall = TRUE) 

t2_overall <- print(out2)

# Create row labels
t2lab <- c("N", "Illness", "Trauma", "Immunization", "Routine",
           "Cough", "Rapid breathing", "Fever", "Diarrhea", "Vomiting", "Other",
           "Number of locations visited for this illness (mean (SD))",
            "Travel mode", "Bicycle/Motorcycle", "Bicycle/Motorcycle & Bus", "Bicycle/Motorcycle & Walk", "Bicycle/Motorcycle & Car", "Car & Walk", "Other", "Private or Shared car", "Public mini-van/bus", 
                "Public or private taxi", "Taxi & Bicycle/Motorcycle", "Taxi & Walk", "Walk", "Walk & Bus",
            "Travel time to arrive at clinic", "<30 minutes", "30-60 minutes", "1-2 hours", ">2 hours",
            "Estimated amount of money spent for transport to arrive at clinic", "0 KSH", "1-20 KSH", "21-40 KSH", "41-60 KSH", "61-80 KSH", "81-100 KSH", ">100 KSH",
            "Asthma", "Jaundice", "HIV", "Malnutrition", "Pneumonia", "Diarrhea", "Malaria", "Convulsions/Meningitis")


# Add row labels
rownames(t2_overall) <- c(t2lab)

# Table formatting
t2_ka <- kable(t2_overall, col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center") %>%
  add_indent(c(14:26, 28:31, 33:39)) %>%
  pack_rows("Visit reason (%)", 2, 5) %>%
  pack_rows("Symptoms reported by caregiver (%)", 6, 11) %>%
  pack_rows("Travel to clinic (%)", 12, 39) %>%
  pack_rows("Medical history (%)", 40, 47)
```
`r t2_ka`

# Table 2a: Basic measurements and physical exam. {.tabset}

## Senegal
```{r include=FALSE}
# Specify all the variables you want to treat as factors -- already factored, no need to pass through factor argument
#factorVars <- c()

# Specify all the variables to include
myVars <- c("weight_yn", "weight", "height_yn", "height", "muac_yn", "muac", "wfh_yn", "wfh", "temp_yn", "temp", "hb_yn", "hb")

# CreateTableOne:
out2a <- CreateTableOne(vars = myVars,
                       data = df_sn,
                      # factorVars = factorVars,
                       strata = "facility_name",
                       test = FALSE,
                       addOverall = TRUE) 

t2a_overall <- print(out2a, showAllLevels = TRUE)

# Create row labels
t2alab <- c("N", "Weight recorded (%)", "", "", "Weight (kg, mean (SD))", "Height recorded (%)", "", "Height (cm, mean (SD))", "MUAC recorded (%)", "", "", "MUAC (cm, mean (SD))", 
            "Weight-for-height recorded (%)", "", "WFH (mean (SD))", 
            "Temperature recorded (%)", "", "Temperature (C, mean (SD))", "Hb recorded (%)", "", "", "Hb (g/dL, mean (SD))")


# Add row labels
rownames(t2a_overall) <- c(t2alab)

# Table formatting
t2a_sn <- kable(t2a_overall, col.names = c(" ", "Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center")
```
`r t2a_sn`

## Tanzania
```{r include=FALSE}
# Specify all the variables you want to treat as factors -- already factored, no need to pass through factor argument
#factorVars <- c()

# Specify all the variables to include
myVars <- c("weight_yn", "weight", "height_yn", "height", "muac_yn", "muac", "wfh_yn", "temp_yn", "temp", "hb_yn", "hb")

# CreateTableOne:
out2a <- CreateTableOne(vars = myVars,
                       data = df_tz,
                      # factorVars = factorVars,
                       strata = "facility_name",
                       test = FALSE,
                       addOverall = TRUE) 

t2a_overall <- print(out2a, showAllLevels = TRUE)

# Create row labels
t2alab <- c("N", "Weight recorded (%)", "", "", "Weight (kg, mean (SD))", "Height recorded (%)", "", "Height (cm, mean (SD))", "MUAC recorded (%)", "", "", "MUAC (cm, mean (SD))", 
            "Weight-for-height recorded (%)", "", 
            "Temperature recorded (%)", "", "Temperature (C, mean (SD))", "Hb recorded (%)", "", "", "Hb (g/dL, mean (SD))")


# Add row labels
rownames(t2a_overall) <- c(t2alab)

# Table formatting
t2a_tz <- kable(t2a_overall, col.names = c(" ", "Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center")
```
`r t2a_tz`

## Kenya
```{r include=FALSE}
# Specify all the variables you want to treat as factors -- already factored, no need to pass through factor argument
#factorVars <- c()

# Specify all the variables to include
myVars <- c("weight_yn", "weight", "height_yn", "height", "muac_yn", "muac", "wfh_yn", "wfh", "temp_yn", "temp", "hb_yn", "hb")

# CreateTableOne:
out2a <- CreateTableOne(vars = myVars,
                       data = df_ka,
                       factorVars = factorVars,
                       strata = "facility_name",
                       test = FALSE,
                       addOverall = TRUE) 

t2a_overall <- print(out2a, showAllLevels = TRUE)

# Create row labels
t2alab <- c("N", "Weight recorded (%)", "", "", "Weight (kg, mean (SD))", "Height recorded (%)", "", "Height (cm, mean (SD))", "MUAC recorded (%)", "", "", "MUAC (cm, mean (SD))", 
            "Weight-for-height recorded (%)", "", "WFH (mean (SD))", 
            "Temperature recorded (%)", "", "Temperature (C, mean (SD))", "Hb recorded (%)", "", "", "Hb (g/dL, mean (SD))")


# Add row labels
rownames(t2a_overall) <- c(t2alab)

# Table formatting
t2a_ka <- kable(t2a_overall, col.names = c(" ", "Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center")
```
`r t2a_ka`

# Table 3: Use of PO device across facilities. {.tabset}

## Senegal
```{r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("used_po_yn", "clinical_measures_complete")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("used_po_yn", "correct_use_yn", "po_duration_min", "consult_duration_min", "clinical_measures_complete")

t3lab <- c("N", "Used PO device during encounter (%)", 
           "PO device used correctly (%)", "No", "Yes", "Yes for some measurements but not all", 
           "Duration of PO device use, minutes (mean (SD))", 
           "Consult duration, minutes (mean (SD))", 
           "All clinical measures (SpO2, PR, RR, Temp) collected (%)")

out3 <- CreateTableOne(vars = myVars,
               data = df_sn,
               factorVars = factorVars,
               strata = "facility_name",
               test = FALSE,
               addOverall = TRUE)
out3_overall <- print(out3)
rownames(out3_overall) <- c(t3lab) # Add row labels

t3_sn <- kable(out3_overall, col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center") %>%
  add_indent(4:6)
```
`r t3_sn`

The PO device was used consistently across encounters except for:

* `r sum(df_sn$no_po_reason==1, na.rm = T)` instances where the device was broken
* `r sum(df_sn$no_po_reason==2, na.rm = T)` instances where the battery was not charged
* `r sum(df_sn$no_po_reason==3, na.rm = T)` instances where the device was being used in another part of the facility
* `r sum(df_sn$no_po_reason==4, na.rm = T)` instances where the device was missing
* `r sum(df_sn$no_po_reason==5, na.rm = T)` instances where the child was too fussy
* `r sum(df_sn$no_po_reason==6, na.rm = T)` instances where the caregiver did not want it
* `r sum(df_sn$no_po_reason==7, na.rm = T)` instances where the provider decided it was not needed

## Tanzania
```{r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("used_po_yn", "clinical_measures_complete")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("used_po_yn", "correct_use_yn", "po_duration_min", "consult_duration_min", "clinical_measures_complete")

t3lab <- c("N", "Used PO device during encounter (%)", 
           "PO device used correctly (%)", "No", "Yes", "Yes for some measurements but not all", 
           "Duration of PO device use, minutes (mean (SD))", 
           "Consult duration, minutes (mean (SD))", 
           "All clinical measures (SpO2, PR, RR, Temp) collected (%)")

out3 <- CreateTableOne(vars = myVars,
               data = df_tz,
               factorVars = factorVars,
               strata = "facility_name",
               test = FALSE,
               addOverall = TRUE)
out3_overall <- print(out3)
rownames(out3_overall) <- c(t3lab) # Add row labels

t3_tz <- kable(out3_overall, col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center") %>%
  add_indent(4:6)
```
`r t3_tz`

The PO device was used consistently across encounters except for:

* `r sum(df_tz$no_po_reason==1, na.rm = T)` instances where the device was broken
* `r sum(df_tz$no_po_reason==2, na.rm = T)` instances where the battery was not charged
* `r sum(df_tz$no_po_reason==3, na.rm = T)` instances where the device was being used in another part of the facility
* `r sum(df_tz$no_po_reason==4, na.rm = T)` instances where the device was missing
* `r sum(df_tz$no_po_reason==5, na.rm = T)` instances where the child was too fussy
* `r sum(df_tz$no_po_reason==6, na.rm = T)` instances where the caregiver did not want it
* `r sum(df_tz$no_po_reason==7, na.rm = T)` instances where the provider decided it was not needed

## Kenya
```{r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("used_po_yn", "clinical_measures_complete")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("used_po_yn", "correct_use_yn", "po_duration_min", "consult_duration_min", "clinical_measures_complete")

t3lab <- c("N", "Used PO device during encounter (%)", 
           "PO device used correctly (%)", "No", "Yes", "Yes for some measurements but not all", 
           "Duration of PO device use, minutes (mean (SD))", 
           "Consult duration, minutes (mean (SD))", 
           "All clinical measures (SpO2, PR, RR, Temp) collected (%)")

out3 <- CreateTableOne(vars = myVars,
               data = df_ka,
               factorVars = factorVars,
               strata = "facility_name",
               test = FALSE,
               addOverall = TRUE)
out3_overall <- print(out3)
rownames(out3_overall) <- c(t3lab) # Add row labels

t3_ka <- kable(out3_overall, col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center") %>%
  add_indent(4:6)
```
`r t3_ka`

The PO device was used consistently across encounters except for:

* `r sum(df_ka$no_po_reason==1, na.rm = T)` instances where the device was broken
* `r sum(df_ka$no_po_reason==2, na.rm = T)` instances where the battery was not charged
* `r sum(df_ka$no_po_reason==3, na.rm = T)` instances where the device was being used in another part of the facility
* `r sum(df_ka$no_po_reason==4, na.rm = T)` instances where the device was missing
* `r sum(df_ka$no_po_reason==5, na.rm = T)` instances where the child was too fussy
* `r sum(df_ka$no_po_reason==6, na.rm = T)` instances where the caregiver did not want it
* `r sum(df_ka$no_po_reason==7, na.rm = T)` instances where the provider decided it was not needed

# Table 4: IMCI classifications per treating provider. {.tabset}

## Senegal {.tabset}

### 0-1 month
```{r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn", "diarrhea_dx_yn", "fever_dx_yn", "ear_dx_yn", "malnutrition_dx_yn", "anemia_dx_yn", "hiv_dx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn","cough_dx", "diarrhea_dx_yn", "diarrhea_dx", "fever_dx_yn", "fever_dx", "ear_dx_yn", "ear_dx", "malnutrition_dx_yn", "malnutrition_dx", "anemia_dx_yn", "anemia_dx", "hiv_dx_yn", "hiv_dx")

t4lab <- c("N", "All main symptoms assessed by provider (%)",
           "All danger signs assessed by provider (%)",
           "Dx given for cough/shortness of breath (%)", "Cough or shortness of breath classification (%)", "Green", "Yellow", "Red",
           "Dx given for diarrhea (%)", "Diarrhea classification (%)", "Green", "Yellow", "Red",
           "Dx given for fever (%)", "Fever classification(%)", "Green", "Yellow", "Red",
           "Dx given for ear problem (%)", "Ear problem classification (%)", "Green", "Yellow", "Red",
           "Dx given for malnutrition (%)", "Malnutrition classification (%)", "Green", "Yellow", "Red",
           "Dx given for anemia (%)", "Anemia classification (%)", "Green", "Yellow", "Red",
           "Dx given for HIV (%)", "HIV classification (%)", "Green", "Yellow", "Red")

out4 <- CreateTableOne(vars = myVars,
               data = df_sn_cat1,
               factorVars = factorVars,
               strata = "facility_name",
               test = FALSE,
               addOverall = TRUE)
out4_overall <- print(out4)
rownames(out4_overall) <- c(t4lab) # Add row labels

t4_sn_cat1 <- kable(print(out4_overall), col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("hover","condensed"), position = "center") %>%
  add_indent(c(6:8, 11:13, 16:18, 21:23, 26:28, 31:33, 36:38)) %>%
  pack_rows("Cough/Shortness of breath", 4, 8) %>%
  pack_rows("Diarrhea", 9, 13) %>%
  pack_rows("Fever", 14, 18) %>%
  pack_rows("Ear problem", 19, 23) %>%
  pack_rows("Malnutrition", 24, 28) %>%
  pack_rows("Anemia", 29, 33) %>%
  pack_rows("HIV", 34, 38) %>%
  row_spec(6, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(7, bold = T, color = "#eda702", background = "white") %>%
  row_spec(8, bold = T,color = "salmon", background = "white") %>%
  row_spec(11, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(12, bold = T, color = "#eda702", background = "white") %>%
  row_spec(13, bold = T,color = "salmon", background = "white") %>%
  row_spec(16, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(17, bold = T, color = "#eda702", background = "white") %>%
  row_spec(18, bold = T,color = "salmon", background = "white") %>%
  row_spec(21, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(22, bold = T, color = "#eda702", background = "white") %>%
  row_spec(23, bold = T,color = "salmon", background = "white") %>%
  row_spec(26, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(27, bold = T, color = "#eda702", background = "white") %>%
  row_spec(28, bold = T,color = "salmon", background = "white") %>%
  row_spec(31, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(32, bold = T, color = "#eda702", background = "white") %>%
  row_spec(33, bold = T,color = "salmon", background = "white") %>%
  row_spec(36, bold = T, color = "#0cbd06", background = "white")  %>%
  row_spec(37, bold = T, color = "#eda702", background = "white") %>%
  row_spec(38, bold = T,color = "salmon", background = "white")
```
`r t4_sn_cat1`

### 2-59 months
```{r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn", "diarrhea_dx_yn", "fever_dx_yn", "ear_dx_yn", "malnutrition_dx_yn", "anemia_dx_yn", "hiv_dx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn","cough_dx", "diarrhea_dx_yn", "diarrhea_dx", "fever_dx_yn", "fever_dx", "ear_dx_yn", "ear_dx", "malnutrition_dx_yn", "malnutrition_dx", "anemia_dx_yn", "anemia_dx", "hiv_dx_yn", "hiv_dx")

t4lab <- c("N", "All main symptoms assessed by provider (%)",
           "All danger signs assessed by provider (%)",
           "Dx given for cough/shortness of breath (%)", "Cough or shortness of breath classification (%)", "Green", "Yellow", "Red",
           "Dx given for diarrhea (%)", "Diarrhea classification (%)", "Green", "Yellow", "Red",
           "Dx given for fever (%)", "Fever classification(%)", "Green", "Yellow", "Red",
           "Dx given for ear problem (%)", "Ear problem classification (%)", "Green", "Yellow", "Red",
           "Dx given for malnutrition (%)", "Malnutrition classification (%)", "Green", "Yellow", "Red",
           "Dx given for anemia (%)", "Anemia classification (%)", "Green", "Yellow", "Red",
           "Dx given for HIV (%)", "HIV classification (%)", "Green", "Yellow", "Red")

out4 <- CreateTableOne(vars = myVars,
               data = df_sn_cat2,
               factorVars = factorVars,
               strata = "facility_name",
               test = FALSE,
               addOverall = TRUE)
out4_overall <- print(out4)
rownames(out4_overall) <- c(t4lab) # Add row labels

t4_sn_cat2 <- kable(print(out4_overall), col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("hover","condensed"), position = "center") %>%
  add_indent(c(6:8, 11:13, 16:18, 21:23, 26:28, 31:33, 36:38)) %>%
  pack_rows("Cough/Shortness of breath", 4, 8) %>%
  pack_rows("Diarrhea", 9, 13) %>%
  pack_rows("Fever", 14, 18) %>%
  pack_rows("Ear problem", 19, 23) %>%
  pack_rows("Malnutrition", 24, 28) %>%
  pack_rows("Anemia", 29, 33) %>%
  pack_rows("HIV", 34, 38) %>%
  row_spec(6, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(7, bold = T, color = "#eda702", background = "white") %>%
  row_spec(8, bold = T,color = "salmon", background = "white") %>%
  row_spec(11, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(12, bold = T, color = "#eda702", background = "white") %>%
  row_spec(13, bold = T,color = "salmon", background = "white") %>%
  row_spec(16, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(17, bold = T, color = "#eda702", background = "white") %>%
  row_spec(18, bold = T,color = "salmon", background = "white") %>%
  row_spec(21, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(22, bold = T, color = "#eda702", background = "white") %>%
  row_spec(23, bold = T,color = "salmon", background = "white") %>%
  row_spec(26, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(27, bold = T, color = "#eda702", background = "white") %>%
  row_spec(28, bold = T,color = "salmon", background = "white") %>%
  row_spec(31, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(32, bold = T, color = "#eda702", background = "white") %>%
  row_spec(33, bold = T,color = "salmon", background = "white") %>%
  row_spec(36, bold = T, color = "#0cbd06", background = "white")  %>%
  row_spec(37, bold = T, color = "#eda702", background = "white") %>%
  row_spec(38, bold = T,color = "salmon", background = "white")
```
`r t4_sn_cat2`

## Tanzania {.tabset}

### 0-1 month
```{r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn", "diarrhea_dx_yn", "fever_dx_yn", "ear_dx_yn", "malnutrition_dx_yn", "anemia_dx_yn", "hiv_dx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn","cough_dx", "diarrhea_dx_yn", "diarrhea_dx", "fever_dx_yn", "fever_dx", "ear_dx_yn", "ear_dx", "malnutrition_dx_yn", "malnutrition_dx", "anemia_dx_yn", "anemia_dx", "hiv_dx_yn", "hiv_dx")

t4lab <- c("N", "All main symptoms assessed by provider (%)",
           "All danger signs assessed by provider (%)",
           "Dx given for cough/shortness of breath (%)", "Cough or shortness of breath classification (%)", "Green", "Yellow", "Red",
           "Dx given for diarrhea (%)", "Diarrhea classification (%)", "Green", "Yellow", "Red",
           "Dx given for fever (%)", "Fever classification(%)", "Green", "Yellow", "Red",
           "Dx given for ear problem (%)", "Ear problem classification (%)", "Green", "Yellow", "Red",
           "Dx given for malnutrition (%)", "Malnutrition classification (%)", "Green", "Yellow", "Red",
           "Dx given for anemia (%)", "Anemia classification (%)", "Green", "Yellow", "Red",
           "Dx given for HIV (%)", "HIV classification (%)", "Green", "Yellow", "Red")

out4 <- CreateTableOne(vars = myVars,
               data = df_tz_cat1,
               factorVars = factorVars,
               strata = "facility_name",
               test = FALSE,
               addOverall = TRUE)
out4_overall <- print(out4)
rownames(out4_overall) <- c(t4lab) # Add row labels

t4_tz_cat1 <- kable(print(out4_overall), col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("hover","condensed"), position = "center") %>%
  add_indent(c(6:8, 11:13, 16:18, 21:23, 26:28, 31:33, 36:38)) %>%
  pack_rows("Cough/Shortness of breath", 4, 8) %>%
  pack_rows("Diarrhea", 9, 13) %>%
  pack_rows("Fever", 14, 18) %>%
  pack_rows("Ear problem", 19, 23) %>%
  pack_rows("Malnutrition", 24, 28) %>%
  pack_rows("Anemia", 29, 33) %>%
  pack_rows("HIV", 34, 38) %>%
  row_spec(6, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(7, bold = T, color = "#eda702", background = "white") %>%
  row_spec(8, bold = T,color = "salmon", background = "white") %>%
  row_spec(11, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(12, bold = T, color = "#eda702", background = "white") %>%
  row_spec(13, bold = T,color = "salmon", background = "white") %>%
  row_spec(16, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(17, bold = T, color = "#eda702", background = "white") %>%
  row_spec(18, bold = T,color = "salmon", background = "white") %>%
  row_spec(21, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(22, bold = T, color = "#eda702", background = "white") %>%
  row_spec(23, bold = T,color = "salmon", background = "white") %>%
  row_spec(26, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(27, bold = T, color = "#eda702", background = "white") %>%
  row_spec(28, bold = T,color = "salmon", background = "white") %>%
  row_spec(31, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(32, bold = T, color = "#eda702", background = "white") %>%
  row_spec(33, bold = T,color = "salmon", background = "white") %>%
  row_spec(36, bold = T, color = "#0cbd06", background = "white")  %>%
  row_spec(37, bold = T, color = "#eda702", background = "white") %>%
  row_spec(38, bold = T,color = "salmon", background = "white")
```
`r t4_tz_cat1`

### 2-59 months
```{r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn", "diarrhea_dx_yn", "fever_dx_yn", "ear_dx_yn", "malnutrition_dx_yn", "anemia_dx_yn", "hiv_dx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn","cough_dx", "diarrhea_dx_yn", "diarrhea_dx", "fever_dx_yn", "fever_dx", "ear_dx_yn", "ear_dx", "malnutrition_dx_yn", "malnutrition_dx", "anemia_dx_yn", "anemia_dx", "hiv_dx_yn", "hiv_dx")

t4lab <- c("N", "All main symptoms assessed by provider (%)",
           "All danger signs assessed by provider (%)",
           "Dx given for cough/shortness of breath (%)", "Cough or shortness of breath classification (%)", "Green", "Yellow", "Red",
           "Dx given for diarrhea (%)", "Diarrhea classification (%)", "Green", "Yellow", "Red",
           "Dx given for fever (%)", "Fever classification(%)", "Green", "Yellow", "Red",
           "Dx given for ear problem (%)", "Ear problem classification (%)", "Green", "Yellow", "Red",
           "Dx given for malnutrition (%)", "Malnutrition classification (%)", "Green", "Yellow", "Red",
           "Dx given for anemia (%)", "Anemia classification (%)", "Green", "Yellow", "Red",
           "Dx given for HIV (%)", "HIV classification (%)", "Green", "Yellow", "Red")

out4 <- CreateTableOne(vars = myVars,
               data = df_tz_cat2,
               factorVars = factorVars,
               strata = "facility_name",
               test = FALSE,
               addOverall = TRUE)
out4_overall <- print(out4)
rownames(out4_overall) <- c(t4lab) # Add row labels

t4_tz_cat2 <- kable(print(out4_overall), col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("hover","condensed"), position = "center") %>%
  add_indent(c(6:8, 11:13, 16:18, 21:23, 26:28, 31:33, 36:38)) %>%
  pack_rows("Cough/Shortness of breath", 4, 8) %>%
  pack_rows("Diarrhea", 9, 13) %>%
  pack_rows("Fever", 14, 18) %>%
  pack_rows("Ear problem", 19, 23) %>%
  pack_rows("Malnutrition", 24, 28) %>%
  pack_rows("Anemia", 29, 33) %>%
  pack_rows("HIV", 34, 38) %>%
  row_spec(6, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(7, bold = T, color = "#eda702", background = "white") %>%
  row_spec(8, bold = T,color = "salmon", background = "white") %>%
  row_spec(11, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(12, bold = T, color = "#eda702", background = "white") %>%
  row_spec(13, bold = T,color = "salmon", background = "white") %>%
  row_spec(16, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(17, bold = T, color = "#eda702", background = "white") %>%
  row_spec(18, bold = T,color = "salmon", background = "white") %>%
  row_spec(21, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(22, bold = T, color = "#eda702", background = "white") %>%
  row_spec(23, bold = T,color = "salmon", background = "white") %>%
  row_spec(26, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(27, bold = T, color = "#eda702", background = "white") %>%
  row_spec(28, bold = T,color = "salmon", background = "white") %>%
  row_spec(31, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(32, bold = T, color = "#eda702", background = "white") %>%
  row_spec(33, bold = T,color = "salmon", background = "white") %>%
  row_spec(36, bold = T, color = "#0cbd06", background = "white")  %>%
  row_spec(37, bold = T, color = "#eda702", background = "white") %>%
  row_spec(38, bold = T,color = "salmon", background = "white")
```
`r t4_tz_cat2`

## Kenya {.tabset}

### 0-1 month
```{r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn", "diarrhea_dx_yn", "fever_dx_yn", "ear_dx_yn", "malnutrition_dx_yn", "anemia_dx_yn", "hiv_dx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn","cough_dx", "diarrhea_dx_yn", "diarrhea_dx", "fever_dx_yn", "fever_dx", "ear_dx_yn", "ear_dx", "malnutrition_dx_yn", "malnutrition_dx", "anemia_dx_yn", "anemia_dx", "hiv_dx_yn")

t4lab <- c("N", "All main symptoms assessed by provider (%)",
           "All danger signs assessed by provider (%)",
           "Dx given for cough/shortness of breath (%)", "Cough or shortness of breath classification (%)", "Green", "Yellow", "Red",
           "Dx given for diarrhea (%)", "Diarrhea classification (%)", "Green", "Yellow", "Red",
           "Dx given for fever (%)", "Fever classification(%)", "Green", "Yellow", "Red",
           "Dx NOT GIVEN for ear problem (%)",
           "Dx NOT GIVEN for malnutrition (%)",
           "Dx NOT GIVEN for anemia (%)",
           "Dx NOT GIVEN for HIV (%)")

out4 <- CreateTableOne(vars = myVars,
               data = df_ka_cat1,
               factorVars = factorVars,
               strata = "facility_name",
               test = FALSE,
               addOverall = TRUE)
out4_overall <- print(out4)
rownames(out4_overall) <- c(t4lab) # Add row labels

t4_ka_cat1 <- kable(print(out4_overall), col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("hover","condensed"), position = "center") %>%
  add_indent(c(6:8, 11:13, 16:18)) %>%
  pack_rows("Cough/Shortness of breath", 4, 8) %>%
  pack_rows("Diarrhea", 9, 13) %>%
  pack_rows("Fever", 14, 18) %>%
  pack_rows("Ear problem", 19, 19) %>%
  pack_rows("Malnutrition", 20, 20) %>%
  pack_rows("Anemia", 21, 21) %>%
  pack_rows("HIV", 22, 22) %>%
  row_spec(6, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(7, bold = T, color = "#eda702", background = "white") %>%
  row_spec(8, bold = T,color = "salmon", background = "white") %>%
  row_spec(11, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(12, bold = T, color = "#eda702", background = "white") %>%
  row_spec(13, bold = T,color = "salmon", background = "white") %>%
  row_spec(16, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(17, bold = T, color = "#eda702", background = "white") %>%
  row_spec(18, bold = T,color = "salmon", background = "white") 
```
`r t4_ka_cat1`

### 2-59 months
```{r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn", "diarrhea_dx_yn", "fever_dx_yn", "ear_dx_yn", "malnutrition_dx_yn", "anemia_dx_yn", "hiv_dx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn","cough_dx", "diarrhea_dx_yn", "diarrhea_dx", "fever_dx_yn", "fever_dx", "ear_dx_yn", "ear_dx", "malnutrition_dx_yn", "malnutrition_dx", "anemia_dx_yn", "anemia_dx", "hiv_dx_yn")

t4lab <- c("N", "All main symptoms assessed by provider (%)",
           "All danger signs assessed by provider (%)",
           "Dx given for cough/shortness of breath (%)", "Cough or shortness of breath classification (%)", "Green", "Yellow", "Red",
           "Dx given for diarrhea (%)", "Diarrhea classification (%)", "Green", "Yellow", "Red",
           "Dx given for fever (%)", "Fever classification(%)", "Green", "Yellow", "Red",
           "Dx given for ear problem (%)", "Ear problem classification (%)", "Green", "Yellow", "Red",
           "Dx given for malnutrition (%)", "Malnutrition classification (%)", "Green", "Yellow", "Red",
           "Dx given for anemia (%)", "Anemia classification (%)", "Green", "Yellow", "Red",
           "Dx NOT GIVEN for HIV (%)")

out4 <- CreateTableOne(vars = myVars,
               data = df_ka_cat2,
               factorVars = factorVars,
               strata = "facility_name",
               test = FALSE,
               addOverall = TRUE)
out4_overall <- print(out4)
rownames(out4_overall) <- c(t4lab) # Add row labels

t4_ka_cat2 <- kable(print(out4_overall), col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("hover","condensed"), position = "center") %>%
  add_indent(c(6:8, 11:13, 16:18, 21:23, 26:28, 31:33)) %>%
  pack_rows("Cough/Shortness of breath", 4, 8) %>%
  pack_rows("Diarrhea", 9, 13) %>%
  pack_rows("Fever", 14, 18) %>%
  pack_rows("Ear problem", 19, 23) %>%
  pack_rows("Malnutrition", 24, 28) %>%
  pack_rows("Anemia", 29, 33) %>%
  pack_rows("HIV", 34, 34) %>%
  row_spec(6, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(7, bold = T, color = "#eda702", background = "white") %>%
  row_spec(8, bold = T,color = "salmon", background = "white") %>%
  row_spec(11, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(12, bold = T, color = "#eda702", background = "white") %>%
  row_spec(13, bold = T,color = "salmon", background = "white") %>%
  row_spec(16, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(17, bold = T, color = "#eda702", background = "white") %>%
  row_spec(18, bold = T,color = "salmon", background = "white") %>%
  row_spec(21, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(22, bold = T, color = "#eda702", background = "white") %>%
  row_spec(23, bold = T,color = "salmon", background = "white") %>%
  row_spec(26, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(27, bold = T, color = "#eda702", background = "white") %>%
  row_spec(28, bold = T,color = "salmon", background = "white") %>%
  row_spec(31, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(32, bold = T, color = "#eda702", background = "white") %>%
  row_spec(33, bold = T,color = "salmon", background = "white")
```
`r t4_ka_cat2`

# Table 5: Clinical outcomes following implementation of PO device. {.tabset}
Thresholds used are as follows (as defined in SAP):

- Hypoxia:
  +	90 < SpO2 < 92% (mild)
  +	88 < SpO2  90% (moderate)
  +	 88% (severe)
  
- Fever: `>`37.5C

- Fast breathing: 
  + <12 months
    +	`>`49 bpm
  + 12-35 months
    +	`>`39 bpm
  + 36-60 months
    +	`>`29 bpm

- Tachycardia: 
  + <12 months
    +	`>`179 bpm 
  + 12-60 months
    +	`>`139 bpm

## Senegal {.tabset}

### 0-1 month
```{r include=FALSE}
# Specify all the variables you want to treat as factors -- note: lab_yn not collected in senegal but should be added in kenya and tanzania
factorVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia", "abx_yn", "rx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia","abx_yn", "rx_yn", "referral")

t5lab <- c("N", "Mild hypoxia - NONE (%)", "Moderate hypoxia - NONE (%)", "Severe hypoxia - NONE (%)", "Fever (%)", "Fast breathing (%)", "Tachycardia - NONE (%)", 
           "Antibiotics given (%)", "Other prescriptions given (%)",
           "Referral advice (%)", "Urgent", "Non-urgent", "Recorded, not readable", "Recorded, no referral")

out5 <- CreateTableOne(vars = myVars,
               data = df_sn_cat1,
               factorVars = factorVars,
               strata = "facility_name",
               test = FALSE,
               addOverall = TRUE)
out5_overall <- print(out5)
rownames(out5_overall) <- c(t5lab) # Add row labels

t5_sn_cat1 <- kable(print(out5_overall), col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center") %>%
  add_indent(11:14) %>%
  pack_rows("Clinical outcomes identified", 2, 7) %>%
  pack_rows("Treatment and referrals", 8, 14)
```
`r t5_sn_cat1`

### 2-59 months
```{r include=FALSE}
# Specify all the variables you want to treat as factors -- note: lab_yn not collected in senegal but should be added in kenya and tanzania
factorVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia", "abx_yn", "rx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia","abx_yn", "rx_yn", "referral")

t5lab <- c("N", "Mild hypoxia (%)", "Moderate hypoxia - NONE (%)", "Severe hypoxia (%)", "Fever (%)", "Fast breathing (%)", "Tachycardia (%)", 
           "Antibiotics given (%)", "Other prescriptions given (%)",
           "Referral advice (%)", "Urgent", "Non-urgent", "Recorded, not readable", "Recorded, no referral")

out5 <- CreateTableOne(vars = myVars,
               data = df_sn_cat2,
               factorVars = factorVars,
               strata = "facility_name",
               test = FALSE,
               addOverall = TRUE)
out5_overall <- print(out5)
rownames(out5_overall) <- c(t5lab) # Add row labels

t5_sn_cat2 <- kable(print(out5_overall), col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center") %>%
  add_indent(11:14) %>%
  pack_rows("Clinical outcomes identified", 2, 7) %>%
  pack_rows("Treatment and referrals", 8, 14)
```
`r t5_sn_cat2`

## Tanzania {.tabset}

### 0-1 month
```{r include=FALSE}
# Specify all the variables you want to treat as factors -- note: lab_yn not collected in senegal but should be added in kenya and tanzania
factorVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia", "abx_yn", "rx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia","abx_yn", "rx_yn", "referral")

t5lab <- c("N", "Mild hypoxia - NONE (%)", "Moderate hypoxia (%)", "Severe hypoxia (%)","Fever (%)", "Fast breathing - NONE (%)", "Tachycardia - NONE (%)", 
           "Antibiotics given (%)", "Other prescriptions given (%)",
           "Referral advice (%)", "Urgent", "Non-urgent", "Recorded, not readable", "Recorded, no referral")

out5 <- CreateTableOne(vars = myVars,
               data = df_tz_cat1,
               factorVars = factorVars,
               strata = "facility_name",
               test = FALSE,
               addOverall = TRUE)
out5_overall <- print(out5)
rownames(out5_overall) <- c(t5lab) # Add row labels

t5_tz_cat1 <- kable(print(out5_overall), col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center") %>%
  add_indent(11:14) %>%
  pack_rows("Clinical outcomes identified", 2, 7) %>%
  pack_rows("Treatment and referrals", 8, 14)
```
`r t5_tz_cat1`

### 2-59 months
```{r include=FALSE}
# Specify all the variables you want to treat as factors -- note: lab_yn not collected in senegal but should be added in kenya and tanzania
factorVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia", "abx_yn", "rx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe","fever", "fast_breathing", "tachycardia","abx_yn", "rx_yn", "referral")

t5lab <- c("N", "Mild hypoxia (%)", "Moderate hypoxia (%)", "Severe hypoxia (%)", "Fever (%)", "Fast breathing (%)", "Tachycardia (%)", 
           "Antibiotics given (%)", "Other prescriptions given (%)",
           "Referral advice (%)", "Urgent", "Non-urgent", "Recorded, not readable", "Recorded, no referral")

out5 <- CreateTableOne(vars = myVars,
               data = df_tz_cat2,
               factorVars = factorVars,
               strata = "facility_name",
               test = FALSE,
               addOverall = TRUE)
out5_overall <- print(out5)
rownames(out5_overall) <- c(t5lab) # Add row labels

t5_tz_cat2 <- kable(print(out5_overall), col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center") %>%
  add_indent(11:14) %>%
  pack_rows("Clinical outcomes identified", 2, 7) %>%
  pack_rows("Treatment and referrals", 8, 14)
```
`r t5_tz_cat2`

## Kenya {.tabset}

### 0-1 month
```{r include=FALSE}
# Specify all the variables you want to treat as factors -- note: lab_yn not collected in senegal but should be added in kenya and tanzania
factorVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia", "abx_yn", "rx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia","abx_yn", "rx_yn", "referral")

t5lab <- c("N", "Mild hypoxia - NONE (%)", "Moderate hypoxia (%)", "Severe hypoxia - NONE (%)", "Fever (%)", "Fast breathing - NONE (%)", "Tachycardia (%)", 
           "Antibiotics given (%)", "Other prescriptions given (%)",
           "Referral advice (%)", "Urgent", "Non-urgent", "Recorded, not readable", "Recorded, no referral")

out5 <- CreateTableOne(vars = myVars,
               data = df_ka_cat1,
               factorVars = factorVars,
               strata = "facility_name",
               test = FALSE,
               addOverall = TRUE)
out5_overall <- print(out5)
rownames(out5_overall) <- c(t5lab) # Add row labels

t5_ka_cat1 <- kable(print(out5_overall), col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center") %>%
  add_indent(11:14) %>%
  pack_rows("Clinical outcomes identified", 2, 7) %>%
  pack_rows("Treatment and referrals", 8, 14)
```
`r t5_ka_cat1`

### 2-59 months
```{r include=FALSE}
# Specify all the variables you want to treat as factors -- note: lab_yn not collected in senegal but should be added in kenya and tanzania
factorVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia", "abx_yn", "rx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia","abx_yn", "rx_yn", "referral")

t5lab <- c("N", "Mild hypoxia (%)", "Moderate hypoxia (%)", "Severe hypoxia (%)", "Fever (%)", "Fast breathing (%)", "Tachycardia (%)", 
           "Antibiotics given (%)", "Other prescriptions given (%)",
           "Referral advice (%)", "Urgent", "Non-urgent", "Recorded, not readable", "Recorded, no referral")

out5 <- CreateTableOne(vars = myVars,
               data = df_ka_cat2,
               factorVars = factorVars,
               strata = "facility_name",
               test = FALSE,
               addOverall = TRUE)
out5_overall <- print(out5)
rownames(out5_overall) <- c(t5lab) # Add row labels

t5_ka_cat2 <- kable(print(out5_overall), col.names = c("Overall", "Facility 1", "Facility 2")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center") %>%
  add_indent(11:14) %>%
  pack_rows("Clinical outcomes identified", 2, 7) %>%
  pack_rows("Treatment and referrals", 8, 14)
```
`r t5_ka_cat2`

# Table 6: Antibiotic prescribed by IMCI classifcations. {.tabset}
## Senegal
```{r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn", "diarrhea_dx_yn", "fever_dx_yn", "ear_dx_yn", "malnutrition_dx_yn", "anemia_dx_yn", "hiv_dx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn","cough_dx", "diarrhea_dx_yn", "diarrhea_dx", "fever_dx_yn", "fever_dx", "ear_dx_yn", "ear_dx", "malnutrition_dx_yn", "malnutrition_dx", "anemia_dx_yn", "anemia_dx", "hiv_dx_yn", "hiv_dx")

t6lab <- c("N", "All main symptoms assessed by provider (%)",
           "All danger signs assessed by provider (%)",
           "Dx given for cough/shortness of breath (%)", "Cough or shortness of breath classification (%)", "Green", "Yellow", "Red",
           "Dx given for diarrhea (%)", "Diarrhea classification (%)", "Green", "Yellow", "Red",
           "Dx given for fever (%)", "Fever classification(%)", "Green", "Yellow", "Red",
           "Dx given for ear problem (%)", "Ear problem classification (%)", "Green", "Yellow", "Red",
           "Dx given for malnutrition (%)", "Malnutrition classification (%)", "Green", "Yellow", "Red",
           "Dx given for anemia (%)", "Anemia classification (%)", "Green", "Yellow", "Red",
           "Dx given for HIV (%)", "HIV classification (%)", "Green", "Yellow", "Red")

out6 <- CreateTableOne(vars = myVars,
               data = df_sn,
               factorVars = factorVars,
               strata = "abx_yn",
               test = FALSE,
               addOverall = TRUE)
out6_overall <- print(out6)
rownames(out6_overall) <- c(t6lab) # Add row labels

t6_sn <- kable(print(out6_overall), col.names = c("Overall", "Not prescribed abx", "Prescribed abx")) %>%
  kable_styling(bootstrap_options=c("hover","condensed"), position = "center") %>%
  add_indent(c(6:8, 11:13, 16:18, 21:23, 26:28, 31:33, 36:38)) %>%
  pack_rows("Cough/Shortness of breath", 4, 8) %>%
  pack_rows("Diarrhea", 9, 13) %>%
  pack_rows("Fever", 14, 18) %>%
  pack_rows("Ear problem", 19, 23) %>%
  pack_rows("Malnutrition", 24, 28) %>%
  pack_rows("Anemia", 29, 33) %>%
  pack_rows("HIV", 34, 38) %>%
  row_spec(6, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(7, bold = T, color = "#eda702", background = "white") %>%
  row_spec(8, bold = T,color = "salmon", background = "white") %>%
  row_spec(11, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(12, bold = T, color = "#eda702", background = "white") %>%
  row_spec(13, bold = T,color = "salmon", background = "white") %>%
  row_spec(16, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(17, bold = T, color = "#eda702", background = "white") %>%
  row_spec(18, bold = T,color = "salmon", background = "white") %>%
  row_spec(21, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(22, bold = T, color = "#eda702", background = "white") %>%
  row_spec(23, bold = T,color = "salmon", background = "white") %>%
  row_spec(26, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(27, bold = T, color = "#eda702", background = "white") %>%
  row_spec(28, bold = T,color = "salmon", background = "white") %>%
  row_spec(31, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(32, bold = T, color = "#eda702", background = "white") %>%
  row_spec(33, bold = T,color = "salmon", background = "white") %>%
  row_spec(36, bold = T, color = "#0cbd06", background = "white")  %>%
  row_spec(37, bold = T, color = "#eda702", background = "white") %>%
  row_spec(38, bold = T,color = "salmon", background = "white")
```
`r t6_sn`

## Tanzania
```{r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn", "diarrhea_dx_yn", "fever_dx_yn", "ear_dx_yn", "malnutrition_dx_yn", "anemia_dx_yn", "hiv_dx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn","cough_dx", "diarrhea_dx_yn", "diarrhea_dx", "fever_dx_yn", "fever_dx", "ear_dx_yn", "ear_dx", "malnutrition_dx_yn", "malnutrition_dx", "anemia_dx_yn", "anemia_dx", "hiv_dx_yn", "hiv_dx")

t6lab <- c("N", "All main symptoms assessed by provider (%)",
           "All danger signs assessed by provider (%)",
           "Dx given for cough/shortness of breath (%)", "Cough or shortness of breath classification (%)", "Green", "Yellow", "Red",
           "Dx given for diarrhea (%)", "Diarrhea classification (%)", "Green", "Yellow", "Red",
           "Dx given for fever (%)", "Fever classification(%)", "Green", "Yellow", "Red",
           "Dx given for ear problem (%)", "Ear problem classification (%)", "Green", "Yellow", "Red",
           "Dx given for malnutrition (%)", "Malnutrition classification (%)", "Green", "Yellow", "Red",
           "Dx given for anemia (%)", "Anemia classification (%)", "Green", "Yellow", "Red",
           "Dx given for HIV (%)", "HIV classification (%)", "Green", "Yellow", "Red")

out6 <- CreateTableOne(vars = myVars,
               data = df_tz,
               factorVars = factorVars,
               strata = "abx_yn",
               test = FALSE,
               addOverall = TRUE)
out6_overall <- print(out6)
rownames(out6_overall) <- c(t6lab) # Add row labels

t6_tz <- kable(print(out6_overall), col.names = c("Overall", "Not prescribed abx", "Prescribed abx")) %>%
  kable_styling(bootstrap_options=c("hover","condensed"), position = "center") %>%
  add_indent(c(6:8, 11:13, 16:18, 21:23, 26:28, 31:33, 36:38)) %>%
  pack_rows("Cough/Shortness of breath", 4, 8) %>%
  pack_rows("Diarrhea", 9, 13) %>%
  pack_rows("Fever", 14, 18) %>%
  pack_rows("Ear problem", 19, 23) %>%
  pack_rows("Malnutrition", 24, 28) %>%
  pack_rows("Anemia", 29, 33) %>%
  pack_rows("HIV", 34, 38) %>%
  row_spec(6, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(7, bold = T, color = "#eda702", background = "white") %>%
  row_spec(8, bold = T,color = "salmon", background = "white") %>%
  row_spec(11, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(12, bold = T, color = "#eda702", background = "white") %>%
  row_spec(13, bold = T,color = "salmon", background = "white") %>%
  row_spec(16, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(17, bold = T, color = "#eda702", background = "white") %>%
  row_spec(18, bold = T,color = "salmon", background = "white") %>%
  row_spec(21, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(22, bold = T, color = "#eda702", background = "white") %>%
  row_spec(23, bold = T,color = "salmon", background = "white") %>%
  row_spec(26, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(27, bold = T, color = "#eda702", background = "white") %>%
  row_spec(28, bold = T,color = "salmon", background = "white") %>%
  row_spec(31, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(32, bold = T, color = "#eda702", background = "white") %>%
  row_spec(33, bold = T,color = "salmon", background = "white") %>%
  row_spec(36, bold = T, color = "#0cbd06", background = "white")  %>%
  row_spec(37, bold = T, color = "#eda702", background = "white") %>%
  row_spec(38, bold = T,color = "salmon", background = "white")
```
`r t6_tz`

## Kenya
``` {r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn", "diarrhea_dx_yn", "fever_dx_yn", "ear_dx_yn", "malnutrition_dx_yn", "anemia_dx_yn", "hiv_dx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn","cough_dx", "diarrhea_dx_yn", "diarrhea_dx", "fever_dx_yn", "fever_dx", "ear_dx_yn", "ear_dx", "malnutrition_dx_yn", "malnutrition_dx", "anemia_dx_yn", "anemia_dx", "hiv_dx_yn")

t6lab <- c("N", "All main symptoms assessed by provider (%)",
           "All danger signs assessed by provider (%)",
           "Dx given for cough/shortness of breath (%)", "Cough or shortness of breath classification (%)", "Green", "Yellow", "Red",
           "Dx given for diarrhea (%)", "Diarrhea classification (%)", "Green", "Yellow", "Red",
           "Dx given for fever (%)", "Fever classification(%)", "Green", "Yellow", "Red",
           "Dx given for ear problem (%)", "Ear problem classification (%)", "Green", "Yellow", "Red",
           "Dx given for malnutrition (%)", "Malnutrition classification (%)", "Green", "Yellow", "Red",
           "Dx given for anemia (%)", "Anemia classification (%)", "Green", "Yellow", "Red",
           "Dx NOT GIVEN for HIV (%)")

out6 <- CreateTableOne(vars = myVars,
               data = df_ka,
               factorVars = factorVars,
               strata = "abx_yn",
               test = FALSE,
               addOverall = TRUE)
out6_overall <- print(out6)
rownames(out6_overall) <- c(t6lab) # Add row labels

t6_ka <- kable(print(out6_overall), col.names = c("Overall", "Not prescribed abx", "Prescribed abx")) %>%
  kable_styling(bootstrap_options=c("hover","condensed"), position = "center") %>%
  add_indent(c(6:8, 11:13, 16:18, 21:23, 26:28, 31:33)) %>%
  pack_rows("Cough/Shortness of breath", 4, 8) %>%
  pack_rows("Diarrhea", 9, 13) %>%
  pack_rows("Fever", 14, 18) %>%
  pack_rows("Ear problem", 19, 23) %>%
  pack_rows("Malnutrition", 24, 28) %>%
  pack_rows("Anemia", 29, 33) %>%
  pack_rows("HIV", 34, 34) %>%
  row_spec(6, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(7, bold = T, color = "#eda702", background = "white") %>%
  row_spec(8, bold = T,color = "salmon", background = "white") %>%
  row_spec(11, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(12, bold = T, color = "#eda702", background = "white") %>%
  row_spec(13, bold = T,color = "salmon", background = "white") %>%
  row_spec(16, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(17, bold = T, color = "#eda702", background = "white") %>%
  row_spec(18, bold = T,color = "salmon", background = "white") %>%
  row_spec(21, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(22, bold = T, color = "#eda702", background = "white") %>%
  row_spec(23, bold = T,color = "salmon", background = "white") %>%
  row_spec(26, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(27, bold = T, color = "#eda702", background = "white") %>%
  row_spec(28, bold = T,color = "salmon", background = "white") %>%
  row_spec(31, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(32, bold = T, color = "#eda702", background = "white") %>%
  row_spec(33, bold = T,color = "salmon", background = "white")
```
`r t6_ka`

# Table 7: Referral by IMCI classifications. {.tabset}
## Senegal
```{r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn", "diarrhea_dx_yn", "fever_dx_yn", "ear_dx_yn", "malnutrition_dx_yn", "anemia_dx_yn", "hiv_dx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn","cough_dx", "diarrhea_dx_yn", "diarrhea_dx", "fever_dx_yn", "fever_dx", "ear_dx_yn", "ear_dx", "malnutrition_dx_yn", "malnutrition_dx", "anemia_dx_yn", "anemia_dx", "hiv_dx_yn", "hiv_dx")

t7lab <- c("N", "All main symptoms assessed by provider (%)",
           "All danger signs assessed by provider (%)",
           "Dx given for cough/shortness of breath (%)", "Cough or shortness of breath classification (%)", "Green", "Yellow", "Red",
           "Dx given for diarrhea (%)", "Diarrhea classification (%)", "Green", "Yellow", "Red",
           "Dx given for fever (%)", "Fever classification(%)", "Green", "Yellow", "Red",
           "Dx given for ear problem (%)", "Ear problem classification (%)", "Green", "Yellow", "Red",
           "Dx given for malnutrition (%)", "Malnutrition classification (%)", "Green", "Yellow", "Red",
           "Dx given for anemia (%)", "Anemia classification (%)", "Green", "Yellow", "Red",
           "Dx given for HIV (%)", "HIV classification (%)", "Green", "Yellow", "Red")

out7 <- CreateTableOne(vars = myVars,
               data = df_sn,
               factorVars = factorVars,
               strata = "referral2",
               test = FALSE,
               addOverall = TRUE)
out7_overall <- print(out7)
rownames(out7_overall) <- c(t7lab) # Add row labels

t7_sn <- kable(print(out7_overall), col.names = c("Overall", "Urgent", "Non-urgent", "No referral")) %>%
  kable_styling(bootstrap_options=c("hover","condensed"), position = "center") %>%
  add_indent(c(6:8, 11:13, 16:18, 21:23, 26:28, 31:33, 36:38)) %>%
  pack_rows("Cough/Shortness of breath", 4, 8) %>%
  pack_rows("Diarrhea", 9, 13) %>%
  pack_rows("Fever", 14, 18) %>%
  pack_rows("Ear problem", 19, 23) %>%
  pack_rows("Malnutrition", 24, 28) %>%
  pack_rows("Anemia", 29, 33) %>%
  pack_rows("HIV", 34, 38) %>%
  row_spec(6, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(7, bold = T, color = "#eda702", background = "white") %>%
  row_spec(8, bold = T,color = "salmon", background = "white") %>%
  row_spec(11, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(12, bold = T, color = "#eda702", background = "white") %>%
  row_spec(13, bold = T,color = "salmon", background = "white") %>%
  row_spec(16, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(17, bold = T, color = "#eda702", background = "white") %>%
  row_spec(18, bold = T,color = "salmon", background = "white") %>%
  row_spec(21, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(22, bold = T, color = "#eda702", background = "white") %>%
  row_spec(23, bold = T,color = "salmon", background = "white") %>%
  row_spec(26, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(27, bold = T, color = "#eda702", background = "white") %>%
  row_spec(28, bold = T,color = "salmon", background = "white") %>%
  row_spec(31, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(32, bold = T, color = "#eda702", background = "white") %>%
  row_spec(33, bold = T,color = "salmon", background = "white") %>%
  row_spec(36, bold = T, color = "#0cbd06", background = "white")  %>%
  row_spec(37, bold = T, color = "#eda702", background = "white") %>%
  row_spec(38, bold = T,color = "salmon", background = "white")
```
`r t7_sn`

## Tanzania
```{r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn", "diarrhea_dx_yn", "fever_dx_yn", "ear_dx_yn", "malnutrition_dx_yn", "anemia_dx_yn", "hiv_dx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn","cough_dx", "diarrhea_dx_yn", "diarrhea_dx", "fever_dx_yn", "fever_dx", "ear_dx_yn", "ear_dx", "malnutrition_dx_yn", "malnutrition_dx", "anemia_dx_yn", "anemia_dx", "hiv_dx_yn", "hiv_dx")

t7lab <- c("N", "All main symptoms assessed by provider (%)",
           "All danger signs assessed by provider (%)",
           "Dx given for cough/shortness of breath (%)", "Cough or shortness of breath classification (%)", "Green", "Yellow", "Red",
           "Dx given for diarrhea (%)", "Diarrhea classification (%)", "Green", "Yellow", "Red",
           "Dx given for fever (%)", "Fever classification(%)", "Green", "Yellow", "Red",
           "Dx given for ear problem (%)", "Ear problem classification (%)", "Green", "Yellow", "Red",
           "Dx given for malnutrition (%)", "Malnutrition classification (%)", "Green", "Yellow", "Red",
           "Dx given for anemia (%)", "Anemia classification (%)", "Green", "Yellow", "Red",
           "Dx given for HIV (%)", "HIV classification (%)", "Green", "Yellow", "Red")

out7 <- CreateTableOne(vars = myVars,
               data = df_tz,
               factorVars = factorVars,
               strata = "referral2",
               test = FALSE,
               addOverall = TRUE)
out7_overall <- print(out7)
rownames(out7_overall) <- c(t7lab) # Add row labels

t7_tz <- kable(print(out7_overall), col.names = c("Overall", "Urgent", "Non-urgent", "No referral")) %>%
  kable_styling(bootstrap_options=c("hover","condensed"), position = "center") %>%
  add_indent(c(6:8, 11:13, 16:18, 21:23, 26:28, 31:33, 36:38)) %>%
  pack_rows("Cough/Shortness of breath", 4, 8) %>%
  pack_rows("Diarrhea", 9, 13) %>%
  pack_rows("Fever", 14, 18) %>%
  pack_rows("Ear problem", 19, 23) %>%
  pack_rows("Malnutrition", 24, 28) %>%
  pack_rows("Anemia", 29, 33) %>%
  pack_rows("HIV", 34, 38) %>%
  row_spec(6, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(7, bold = T, color = "#eda702", background = "white") %>%
  row_spec(8, bold = T,color = "salmon", background = "white") %>%
  row_spec(11, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(12, bold = T, color = "#eda702", background = "white") %>%
  row_spec(13, bold = T,color = "salmon", background = "white") %>%
  row_spec(16, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(17, bold = T, color = "#eda702", background = "white") %>%
  row_spec(18, bold = T,color = "salmon", background = "white") %>%
  row_spec(21, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(22, bold = T, color = "#eda702", background = "white") %>%
  row_spec(23, bold = T,color = "salmon", background = "white") %>%
  row_spec(26, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(27, bold = T, color = "#eda702", background = "white") %>%
  row_spec(28, bold = T,color = "salmon", background = "white") %>%
  row_spec(31, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(32, bold = T, color = "#eda702", background = "white") %>%
  row_spec(33, bold = T,color = "salmon", background = "white") %>%
  row_spec(36, bold = T, color = "#0cbd06", background = "white")  %>%
  row_spec(37, bold = T, color = "#eda702", background = "white") %>%
  row_spec(38, bold = T,color = "salmon", background = "white")
```
`r t7_tz`

## Kenya
``` {r include=FALSE}
# Specify all the variables you want to treat as factors
factorVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn", "diarrhea_dx_yn", "fever_dx_yn", "ear_dx_yn", "malnutrition_dx_yn", "anemia_dx_yn", "hiv_dx_yn")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("mainsxs_assessed_yn", "danger_assessed_yn", "cough_dx_yn","cough_dx", "diarrhea_dx_yn", "diarrhea_dx", "fever_dx_yn", "fever_dx", "ear_dx_yn", "ear_dx", "malnutrition_dx_yn", "malnutrition_dx", "anemia_dx_yn", "anemia_dx", "hiv_dx_yn")

t7lab <- c("N", "All main symptoms assessed by provider (%)",
           "All danger signs assessed by provider (%)",
           "Dx given for cough/shortness of breath (%)", "Cough or shortness of breath classification (%)", "Green", "Yellow", "Red",
           "Dx given for diarrhea (%)", "Diarrhea classification (%)", "Green", "Yellow", "Red",
           "Dx given for fever (%)", "Fever classification(%)", "Green", "Yellow", "Red",
           "Dx given for ear problem (%)", "Ear problem classification (%)", "Green", "Yellow", "Red",
           "Dx given for malnutrition (%)", "Malnutrition classification (%)", "Green", "Yellow", "Red",
           "Dx given for anemia (%)", "Anemia classification (%)", "Green", "Yellow", "Red",
           "Dx NOT GIVEN for HIV (%)")

out7 <- CreateTableOne(vars = myVars,
               data = df_ka,
               factorVars = factorVars,
               strata = "referral2",
               test = FALSE,
               addOverall = TRUE)
out7_overall <- print(out7)
rownames(out7_overall) <- c(t7lab) # Add row labels

t7_ka <- kable(print(out7_overall), col.names = c("Overall", "Urgent", "Non-urgent", "No referral")) %>%
  kable_styling(bootstrap_options=c("hover","condensed"), position = "center") %>%
  add_indent(c(6:8, 11:13, 16:18, 21:23, 26:28, 31:33)) %>%
  pack_rows("Cough/Shortness of breath", 4, 8) %>%
  pack_rows("Diarrhea", 9, 13) %>%
  pack_rows("Fever", 14, 18) %>%
  pack_rows("Ear problem", 19, 23) %>%
  pack_rows("Malnutrition", 24, 28) %>%
  pack_rows("Anemia", 29, 33) %>%
  pack_rows("HIV", 34, 34) %>%
  row_spec(6, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(7, bold = T, color = "#eda702", background = "white") %>%
  row_spec(8, bold = T,color = "salmon", background = "white") %>%
  row_spec(11, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(12, bold = T, color = "#eda702", background = "white") %>%
  row_spec(13, bold = T,color = "salmon", background = "white") %>%
  row_spec(16, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(17, bold = T, color = "#eda702", background = "white") %>%
  row_spec(18, bold = T,color = "salmon", background = "white") %>%
  row_spec(21, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(22, bold = T, color = "#eda702", background = "white") %>%
  row_spec(23, bold = T,color = "salmon", background = "white") %>%
  row_spec(26, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(27, bold = T, color = "#eda702", background = "white") %>%
  row_spec(28, bold = T,color = "salmon", background = "white") %>%
  row_spec(31, bold = T, color = "#0cbd06", background = "white") %>%
  row_spec(32, bold = T, color = "#eda702", background = "white") %>%
  row_spec(33, bold = T,color = "salmon", background = "white")
```
`r t7_ka`

# Table 8: Antiobiotic prescribed by clinical outcomes. {.tabset}
## Senegal
```{r include=FALSE}
factorVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia")

t8lab <- c("N", "Mild hypoxia (%)", "Moderate hypoxia (%)", "Severe hypoxia (%)", "Fever (%)", "Fast breathing (%)", "Tachycardia (%)")

out8 <- CreateTableOne(vars = myVars,
               data = df_sn,
               factorVars = factorVars,
               strata = "abx_yn",
               test = FALSE,
               addOverall = TRUE)
out8_overall <- print(out8)
rownames(out8_overall) <- c(t8lab) # Add row labels

t8_sn <- kable(print(out8_overall), col.names = c("Overall", "Not prescribed abx", "Prescribed abx")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center")
```
`r t8_sn`

## Tanzania
```{r include=FALSE}
factorVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia")

t8lab <- c("N", "Mild hypoxia (%)", "Moderate hypoxia (%)", "Severe hypoxia (%)", "Fever (%)", "Fast breathing (%)", "Tachycardia (%)")

out8 <- CreateTableOne(vars = myVars,
               data = df_tz,
               factorVars = factorVars,
               strata = "abx_yn",
               test = FALSE,
               addOverall = TRUE)
out8_overall <- print(out8)
rownames(out8_overall) <- c(t8lab) # Add row labels

t8_tz <- kable(print(out8_overall), col.names = c("Overall", "Not prescribed abx", "Prescribed abx")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center")
```
`r t8_tz`

## Kenya
```{r include=FALSE}
factorVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia")

t8lab <- c("N", "Mild hypoxia (%)", "Moderate hypoxia (%)", "Severe hypoxia (%)", "Fever (%)", "Fast breathing (%)", "Tachycardia (%)")

out8 <- CreateTableOne(vars = myVars,
               data = df_ka,
               factorVars = factorVars,
               strata = "abx_yn",
               test = FALSE,
               addOverall = TRUE)
out8_overall <- print(out8)
rownames(out8_overall) <- c(t8lab) # Add row labels

t8_ka <- kable(print(out8_overall), col.names = c("Overall", "Not prescribed abx", "Prescribed abx")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center")
```
`r t8_ka`

# Table 9: Referral by clincial outcomes. {.tabset}
## Senegal
```{r include=FALSE}
factorVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia")

t9lab <- c("N", "Mild hypoxia (%)", "Moderate hypoxia (%)", "Severe hypoxia (%)", "Fever (%)", "Fast breathing (%)", "Tachycardia (%)")

out9 <- CreateTableOne(vars = myVars,
               data = df_sn,
               factorVars = factorVars,
               strata = "referral2",
               test = FALSE,
               addOverall = TRUE)
out9_overall <- print(out9)
rownames(out9_overall) <- c(t9lab) # Add row labels

t9_sn <- kable(print(out9_overall), col.names = c("Overall", "Urgent", "Non-urgent", "No referral")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center")
```
`r t9_sn`

## Tanzania
```{r include=FALSE}
factorVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia")

t9lab <- c("N", "Mild hypoxia (%)", "Moderate hypoxia (%)", "Severe hypoxia (%)", "Fever (%)", "Fast breathing (%)", "Tachycardia (%)")

out9 <- CreateTableOne(vars = myVars,
               data = df_tz,
               factorVars = factorVars,
               strata = "referral2",
               test = FALSE,
               addOverall = TRUE)
out9_overall <- print(out9)
rownames(out9_overall) <- c(t9lab) # Add row labels

t9_tz <- kable(print(out9_overall), col.names = c("Overall", "Urgent", "Non-urgent", "No referral")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center")
```
`r t9_tz`

## Kenya
```{r include=FALSE}
factorVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("hypoxia_mild", "hypoxia_moderate", "hypoxia_severe", "fever", "fast_breathing", "tachycardia")

t9lab <- c("N", "Mild hypoxia (%)", "Moderate hypoxia (%)", "Severe hypoxia (%)", "Fever (%)", "Fast breathing (%)", "Tachycardia (%)")

out9 <- CreateTableOne(vars = myVars,
               data = df_ka,
               factorVars = factorVars,
               strata = "referral2",
               test = FALSE,
               addOverall = TRUE)
out9_overall <- print(out9)
rownames(out9_overall) <- c(t9lab) # Add row labels

t9_ka <- kable(print(out9_overall), col.names = c("Overall", "Urgent", "Non-urgent", "No referral")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center")
```
`r t9_ka`

# Indicators of IMCI fidelity {.tabset}

1. Red classification of cough/difficulty breathing receives a referral and antibiotics.
2. Red classification of diarrhea receives treatment for dehydration.
3. Red classification of diarrhea AND red classification of anything else receives a referral.
4. Red classification of fever receives antimalarial or antibiotic treatment and a referral.

## Indicator #1 {.tabset}

### Senegal
#### Patient flow through indicator
```{r}
# Consort
# relevant variables: cough_dx==2 and abx_yn==1 and referral==1 or 2
tdf <- df_sn %>% dplyr:::select(screening_id, cg_report_cough_dyspnea, cough_dyspnea_assessed, cough_dx, abx_yn, referral2)
tdf <- subset(tdf, cg_report_cough_dyspnea==1)
tdf$drop1 <- ifelse(tdf$cough_dyspnea_assessed=="Neither assessed", "Cough/dyspnea not assessed", NA)
tdf$drop2 <- case_when(is.na(tdf$cough_dx) ~ "Not rated",
                        tdf$cough_dx=="Green" ~ "Green",
                        tdf$cough_dx=="Yellow" ~ "Yellow")
tdf$drop2 <- factor(tdf$drop2, levels = c("Green", "Yellow", "Not rated"))
tdf$drop3 <- ifelse(tdf$abx_yn=="No", "Not prescribed", NA)
tdf$drop4 <- ifelse(tdf$referral2=="Recorded as not referred", "Not referred", NA)

consort1_sn <- consort_plot(data = tdf,
                            orders = c(screening_id = "Reported cough or difficulty breathing",
                                       drop1 = "Provider assessment",
                                       screening_id = "Provider assessed cough or difficulty breathing",
                                       drop2 = "Non-severe IMCI classification",
                                       screening_id = "Rated severe cough/difficulty breathing",
                                       drop3 = "Antibiotic status",
                                       screening_id = "Prescribed antibiotic",
                                       drop4 = "Referral status",
                                       screening_id = "Referred"),
                            side_box = c("drop1", "drop2", "drop3", "drop4"),
                            cex = 0.9)
plot(consort1_sn)
```

```{r}
# Sankey
tdf <- df_sn %>% dplyr::select(cg_report_cough_dyspnea, cough_dyspnea_assessed, cough_dx, abx_yn, referral2)
tdf$cg_report_cough_dyspnea <- ifelse(tdf$cg_report_cough_dyspnea==1, "Cough/dyspnea reported", "Cough/dyspnea not reported")
tdf$cg_report_cough_dyspnea <- factor(tdf$cg_report_cough_dyspnea, levels = c("Cough/dyspnea reported", "Cough/dyspnea not reported"))
tdf$referral2 <- case_when(tdf$referral2=="Urgent" ~ "Referral given",
                           tdf$referral2=="Non-urgent" ~ "Referral given",
                           tdf$referral2=="Recorded as not referred" ~ "No referral given",
                           is.na(tdf$referral2) ~ "Unknown")
tdf$cough_dx <- ifelse(is.na(tdf$cough_dx), "Not rated", as.character(tdf$cough_dx))
tdf$cough_dx <- factor(tdf$cough_dx, levels = c("Red", "Yellow", "Green", "Not rated"))
tdf$abx_yn <- case_when(tdf$abx_yn=="Yes" ~ "Antibiotics given",
                        tdf$abx_yn=="No" ~ "No antibiotics given",
                        is.na(tdf$abx_yn) ~ "No antibiotics given")
tdf$referral2 <- factor(tdf$referral2, levels = c("Referral given", "No referral given", "Unknown"))

s1_sn <- highchart() %>% hc_add_series(data_to_sankey(tdf), "sankey", name = "Cough/Dyspnea", hcaes(from = from, to = to, weight = weight),
                      nodes = list(list(id = 'Cough/dyspnea reported'  , color = "#CC6699"),
                                 list(id = 'Cough/dyspnea not reported' , color = "#33CC99"),
                                 list(id = 'Cough or dyspnea assessed' , color = "#33CCCC"),
                                 list(id = 'Neither assessed'   , color = "#CC3333"),
                                 list(id = "Red"  , color = "#FF3333"),
                                 list(id = "Yellow"  , color = "#FFFF66"),
                                 list(id = "Green"    , color = "#33CC33"),
                                 list(id = "Not rated"    , color = "darkgrey"),
                                 list(id = "Antibiotics given"    , color = "#00FF99"),
                                 list(id = "No antibiotics given"    , color = "#FF9999"),
                                 list(id = "Referral given"    , color = "#33CC66"),
                                 list(id = "No referral given"    , color = "#CC6666"),
                                 list(id = "Unknown"    , color = "darkgray")))%>%
                      hc_title(text = "Cough and Dyspnea") %>%
                      hc_subtitle(text = "<em/>Care pathway from reported symptoms through treatment and referral</em>") %>%
                      hc_caption(text = "<b/>Data from Senegal</b>") %>%
                      hc_add_theme(plosgph_theme) %>%
                      hc_plotOptions(series = list(dataLabels = list(style = list(fontSize = "11px"))))
s1_sn
```

### Tanzania 
#### Patient flow through indicator
```{r}
# Consort
# relevant variables: cough_dx==2 and abx_yn==1 and referral==1 or 2
tdf <- df_tz %>% dplyr:::select(screening_id, cg_report_cough_dyspnea, cough_dyspnea_assessed, cough_dx, abx_yn, referral2)
tdf <- subset(tdf, cg_report_cough_dyspnea==1)
tdf$drop1 <- ifelse(tdf$cough_dyspnea_assessed=="Neither assessed", "Cough/dyspnea not assessed", NA)
tdf$drop2 <- case_when(is.na(tdf$cough_dx) ~ "Not rated",
                        tdf$cough_dx=="Green" ~ "Green",
                        tdf$cough_dx=="Yellow" ~ "Yellow")
tdf$drop2 <- factor(tdf$drop2, levels = c("Green", "Yellow", "Not rated"))
tdf$drop3 <- ifelse(tdf$abx_yn=="No", "Not prescribed", NA)
tdf$drop4 <- ifelse(tdf$referral2=="Recorded as not referred", "Not referred", NA)

consort1_tz <- consort_plot(data = tdf,
                            orders = c(screening_id = "Reported cough or difficulty breathing",
                                       drop1 = "Provider assessment",
                                       screening_id = "Provider assessed cough or difficulty breathing",
                                       drop2 = "Non-severe IMCI classification",
                                       screening_id = "Rated severe cough/difficulty breathing",
                                       drop3 = "Antibiotic status",
                                       screening_id = "Prescribed antibiotic",
                                       drop4 = "Referral status",
                                       screening_id = "Referred"),
                            side_box = c("drop1", "drop2", "drop3", "drop4"),
                            cex = 0.9)
plot(consort1_tz)
```

```{r}
# Sankey
tdf <- df_tz %>% dplyr::select(cg_report_cough_dyspnea, cough_dyspnea_assessed, cough_dx, abx_yn, referral2)
tdf$cg_report_cough_dyspnea <- ifelse(tdf$cg_report_cough_dyspnea==1, "Cough/dyspnea reported", "Cough/dyspnea not reported")
tdf$cg_report_cough_dyspnea <- factor(tdf$cg_report_cough_dyspnea, levels = c("Cough/dyspnea reported", "Cough/dyspnea not reported"))
tdf$referral2 <- case_when(tdf$referral2=="Urgent" ~ "Referral given",
                           tdf$referral2=="Non-urgent" ~ "Referral given",
                           tdf$referral2=="Recorded as not referred" ~ "No referral given",
                           is.na(tdf$referral2) ~ "Unknown")
tdf$cough_dx <- ifelse(is.na(tdf$cough_dx), "Not rated", as.character(tdf$cough_dx))
tdf$cough_dx <- factor(tdf$cough_dx, levels = c("Red", "Yellow", "Green", "Not rated"))
tdf$abx_yn <- case_when(tdf$abx_yn=="Yes" ~ "Antibiotics given",
                        tdf$abx_yn=="No" ~ "No antibiotics given",
                        is.na(tdf$abx_yn) ~ "No antibiotics given")
tdf$referral2 <- factor(tdf$referral2, levels = c("Referral given", "No referral given", "Unknown"))

s1_tz <- highchart() %>% hc_add_series(data_to_sankey(tdf), "sankey", name = "Cough/Dyspnea", hcaes(from = from, to = to, weight = weight),
                      nodes = list(list(id = 'Cough/dyspnea reported'  , color = "#CC6699"),
                                 list(id = 'Cough/dyspnea not reported' , color = "#33CC99"),
                                 list(id = 'Cough or dyspnea assessed' , color = "#33CCCC"),
                                 list(id = 'Neither assessed'   , color = "#CC3333"),
                                 list(id = "Red"  , color = "#FF3333"),
                                 list(id = "Yellow"  , color = "#FFFF66"),
                                 list(id = "Green"    , color = "#33CC33"),
                                 list(id = "Not rated"    , color = "darkgrey"),
                                 list(id = "Antibiotics given"    , color = "#00FF99"),
                                 list(id = "No antibiotics given"    , color = "#FF9999"),
                                 list(id = "Referral given"    , color = "#33CC66"),
                                 list(id = "No referral given"    , color = "#CC6666"),
                                 list(id = "Unknown"    , color = "darkgray")))%>%
                      hc_title(text = "Cough and Dyspnea") %>%
                      hc_subtitle(text = "<em/>Care pathway from reported symptoms through treatment and referral</em>") %>%
                      hc_caption(text = "<b/>Data from Tanzania</b>") %>%
                      hc_add_theme(plosgph_theme) %>%
                      hc_plotOptions(series = list(dataLabels = list(style = list(fontSize = "11px"))))
s1_tz
```

### Kenya
#### Patient flow through indicator
*Referral/Antibiotic switched here because of N's.*
``` {r}
# Consort
# relevant variables: cough_dx==2 and abx_yn==1 and referral==1 or 2
tdf <- df_ka %>% dplyr:::select(screening_id, cg_report_cough_dyspnea, cough_dyspnea_assessed, cough_dx, abx_yn, referral2)
tdf <- subset(tdf, cg_report_cough_dyspnea==1)
tdf$drop1 <- ifelse(tdf$cough_dyspnea_assessed=="Neither assessed", "Cough/dyspnea not assessed", NA)
tdf$drop2 <- case_when(is.na(tdf$cough_dx) ~ "Not rated",
                        tdf$cough_dx=="Green" ~ "Green",
                        tdf$cough_dx=="Yellow" ~ "Yellow")
tdf$drop2 <- factor(tdf$drop2, levels = c("Green", "Yellow", "Not rated"))
tdf$drop3 <- ifelse(tdf$abx_yn=="No", "Not prescribed", NA)
tdf$drop4 <- ifelse(tdf$referral2=="Recorded as not referred", "Not referred", NA)

consort1_ka <- consort_plot(data = tdf,
                            orders = c(screening_id = "Reported cough or difficulty breathing",
                                       drop1 = "Provider assessment",
                                       screening_id = "Provider assessed cough or difficulty breathing",
                                       drop2 = "Non-severe IMCI classification",
                                       screening_id = "Rated severe cough/difficulty breathing",
                                       drop4 = "Referral status",
                                       screening_id = "Referred",
                                       drop3 = "Antibiotic status",
                                       screening_id = "Prescribed antibiotic"),
                            side_box = c("drop1", "drop2", "drop4", "drop3"),
                            cex = 0.9)
plot(consort1_ka)
```

```{r}
# Sankey
tdf <- df_ka %>% dplyr::select(cg_report_cough_dyspnea, cough_dyspnea_assessed, cough_dx, abx_yn, referral2)
tdf$cg_report_cough_dyspnea <- ifelse(tdf$cg_report_cough_dyspnea==1, "Cough/dyspnea reported", "Cough/dyspnea not reported")
tdf$cg_report_cough_dyspnea <- factor(tdf$cg_report_cough_dyspnea, levels = c("Cough/dyspnea reported", "Cough/dyspnea not reported"))
tdf$referral2 <- case_when(tdf$referral2=="Urgent" ~ "Referral given",
                           tdf$referral2=="Non-urgent" ~ "Referral given",
                           tdf$referral2=="Recorded as not referred" ~ "No referral given",
                           is.na(tdf$referral2) ~ "Unknown")
tdf$cough_dx <- ifelse(is.na(tdf$cough_dx), "Not rated", as.character(tdf$cough_dx))
tdf$cough_dx <- factor(tdf$cough_dx, levels = c("Red", "Yellow", "Green", "Not rated"))
tdf$abx_yn <- case_when(tdf$abx_yn=="Yes" ~ "Antibiotics given",
                        tdf$abx_yn=="No" ~ "No antibiotics given",
                        is.na(tdf$abx_yn) ~ "No antibiotics given")
tdf$referral2 <- factor(tdf$referral2, levels = c("Referral given", "No referral given", "Unknown"))

s1_ka <- highchart() %>% hc_add_series(data_to_sankey(tdf), "sankey", name = "Cough/Dyspnea", hcaes(from = from, to = to, weight = weight),
                      nodes = list(list(id = 'Cough/dyspnea reported'  , color = "#CC6699"),
                                 list(id = 'Cough/dyspnea not reported' , color = "#33CC99"),
                                 list(id = 'Cough or dyspnea assessed' , color = "#33CCCC"),
                                 list(id = 'Neither assessed'   , color = "#CC3333"),
                                 list(id = "Red"  , color = "#FF3333"),
                                 list(id = "Yellow"  , color = "#FFFF66"),
                                 list(id = "Green"    , color = "#33CC33"),
                                 list(id = "Not rated"    , color = "darkgrey"),
                                 list(id = "Antibiotics given"    , color = "#00FF99"),
                                 list(id = "No antibiotics given"    , color = "#FF9999"),
                                 list(id = "Referral given"    , color = "#33CC66"),
                                 list(id = "No referral given"    , color = "#CC6666"),
                                 list(id = "Unknown"    , color = "darkgray")))%>%
                      hc_title(text = "Cough and Dyspnea") %>%
                      hc_subtitle(text = "<em/>Care pathway from reported symptoms through treatment and referral</em>") %>%
                      hc_caption(text = "<b/>Data from Kenya</b>") %>%
                      hc_add_theme(plosgph_theme) %>%
                      hc_plotOptions(series = list(dataLabels = list(style = list(fontSize = "11px"))))
s1_ka
```

## Indicator #2 {.tabset}

### Senegal
#### Patient flow through indicator
```{r}
# Consort
tdf <- df_sn %>% dplyr:::select(screening_id, cg_report_diarrhea, diarrhea_yn, diarrhea_dx, rx___12)
tdf <- subset(tdf, cg_report_diarrhea==1)
tdf$drop1 <- ifelse(tdf$diarrhea_yn==0, "Provider did not assess diarrhea", NA)
tdf$drop2 <- case_when(is.na(tdf$diarrhea_dx) ~ "Not rated",
                        tdf$diarrhea_dx=="Green" ~ "Green",
                        tdf$diarrhea_dx=="Yellow" ~ "Yellow")
tdf$drop2 <- factor(tdf$drop2, levels = c("Green", "Yellow", "Not rated"))
tdf$drop3 <- ifelse(is.na(tdf$rx___12), "Not given", NA)

consort2_sn <- consort_plot(data = tdf,
                            orders = c(screening_id = "Reported diarrhea",
                                       drop1 = "Provider assessment",
                                       screening_id = "Provider assessed diarrhea",
                                       drop2 = "Non-severe IMCI classification",
                                       screening_id = "Rated severe diarrhea",
                                       drop3 = "Treatment status",
                                       screening_id = "Given dehydration treatment"),
                            side_box = c("drop1", "drop2", "drop3"),
                            cex = 0.9)
plot(consort2_sn)
```

```{r}
# Sankey
tdf <- df_sn %>% dplyr::select(cg_report_diarrhea, diarrhea_yn, diarrhea_dx, rx___12)
tdf$cg_report_diarrhea <- ifelse(tdf$cg_report_diarrhea==1, "Diarrhea reported", "Diarrhea not reported")
tdf$cg_report_diarrhea <- factor(tdf$cg_report_diarrhea, levels = c("Diarrhea reported", "Diarrhea not reported"))
tdf$diarrhea_yn <- ifelse(tdf$diarrhea_yn==1, "Provider assessed diarrhea", "Provider did not assess diarrhea")
tdf$diarrhea_dx <- ifelse(is.na(tdf$diarrhea_dx), "Not rated", as.character(tdf$diarrhea_dx))
tdf$diarrhea_dx <- factor(tdf$diarrhea_dx, levels = c("Red", "Yellow", "Green", "Not rated"))
tdf$rx___12 <- ifelse(tdf$rx___12==1, "Dehydration treatment given", "No treatment given")
tdf$rx___12 <- ifelse(is.na(tdf$rx___12), "No treatment given", tdf$rx___12)

s2_sn <- highchart() %>% hc_add_series(data_to_sankey(tdf), "sankey", name = "Diarrhea", hcaes(from = from, to = to, weight = weight),
                      nodes = list(list(id = 'Diarrhea reported'  , color = "#CC6699"),
                                 list(id = 'Diarrhea not reported' , color = "#33CC99"),
                                 list(id = 'Provider assessed diarrhea' , color = "#33CCCC"),
                                 list(id = 'Provider did not assess diarrhea'   , color = "#CC3333"),
                                 list(id = "Red"  , color = "#FF3333"),
                                 list(id = "Yellow"  , color = "#FFFF66"),
                                 list(id = "Green"    , color = "#33CC33"),
                                 list(id = "Not rated"    , color = "darkgrey"),
                                 list(id = "No treatment given"    , color = "#FF9999"))) %>%
                      hc_title(text = "Diarrhea") %>%
                      hc_subtitle(text = "<em/>Care pathway from reported symptoms through treatment</em>") %>%
                      hc_caption(text = "<b/>Data from Senegal</b>") %>%
                      hc_add_theme(plosgph_theme) %>%
                      hc_plotOptions(series = list(dataLabels = list(style = list(fontSize = "11px"))))
s2_sn
```

### Tanzania
#### Patient flow through indicator
```{r}
# Consort
tdf <- df_tz %>% dplyr:::select(screening_id, cg_report_diarrhea, diarrhea_yn, diarrhea_dx, rx___12)
tdf <- subset(tdf, cg_report_diarrhea==1)
tdf$drop1 <- ifelse(tdf$diarrhea_yn==0, "Provider did not assess diarrhea", NA)
tdf$drop2 <- case_when(is.na(tdf$diarrhea_dx) ~ "Not rated",
                        tdf$diarrhea_dx=="Green" ~ "Green",
                        tdf$diarrhea_dx=="Yellow" ~ "Yellow")
tdf$drop2 <- factor(tdf$drop2, levels = c("Green", "Yellow", "Not rated"))
tdf$drop3 <- ifelse(is.na(tdf$rx___12) | tdf$rx___12==0, "Not given", NA)

consort2_tz <- consort_plot(data = tdf,
                            orders = c(screening_id = "Reported diarrhea",
                                       drop1 = "Provider assessment",
                                       screening_id = "Provider assessed diarrhea",
                                       drop2 = "Non-severe IMCI classification",
                                       screening_id = "Rated severe diarrhea",
                                       drop3 = "Treatment status",
                                       screening_id = "Given dehydration treatment"),
                            side_box = c("drop1", "drop2", "drop3"),
                            cex = 0.9)
plot(consort2_tz)
```

```{r}
# Sankey
tdf <- df_tz %>% dplyr::select(cg_report_diarrhea, diarrhea_yn, diarrhea_dx, rx___12)
tdf$cg_report_diarrhea <- ifelse(tdf$cg_report_diarrhea==1, "Diarrhea reported", "Diarrhea not reported")
tdf$cg_report_diarrhea <- factor(tdf$cg_report_diarrhea, levels = c("Diarrhea reported", "Diarrhea not reported"))
tdf$diarrhea_yn <- ifelse(tdf$diarrhea_yn==1, "Provider assessed diarrhea", "Provider did not assess diarrhea")
tdf$diarrhea_dx <- ifelse(is.na(tdf$diarrhea_dx), "Not rated", as.character(tdf$diarrhea_dx))
tdf$diarrhea_dx <- factor(tdf$diarrhea_dx, levels = c("Red", "Yellow", "Green", "Not rated"))
tdf$rx___12 <- ifelse(tdf$rx___12==1, "Dehydration treatment given", "No treatment given")

s2_tz <- highchart() %>% hc_add_series(data_to_sankey(tdf), "sankey", name = "Diarrhea", hcaes(from = from, to = to, weight = weight),
                      nodes = list(list(id = 'Diarrhea reported'  , color = "#CC6699"),
                                 list(id = 'Diarrhea not reported' , color = "#33CC99"),
                                 list(id = 'Provider assessed diarrhea' , color = "#33CCCC"),
                                 list(id = 'Provider did not assess diarrhea'   , color = "#CC3333"),
                                 list(id = "Red"  , color = "#FF3333"),
                                 list(id = "Yellow"  , color = "#FFFF66"),
                                 list(id = "Green"    , color = "#33CC33"),
                                 list(id = "Not rated"    , color = "darkgrey"),
                                 list(id = "Dehydration treatment given"    , color = "#00FF99"),
                                 list(id = "No treatment given"    , color = "#FF9999")))%>%
                      hc_title(text = "Diarrhea") %>%
                      hc_subtitle(text = "<em/>Care pathway from reported symptoms through treatment</em>") %>%
                      hc_caption(text = "<b/>Data from Tanzania</b>") %>%
                      hc_add_theme(plosgph_theme) %>%
                      hc_plotOptions(series = list(dataLabels = list(style = list(fontSize = "11px"))))
s2_tz
```

### Kenya
#### Patient flow through indicator
```{r}
# Consort
tdf <- df_ka %>% dplyr:::select(screening_id, cg_report_diarrhea, diarrhea_yn, diarrhea_dx, rx___12)
tdf <- subset(tdf, cg_report_diarrhea==1)
tdf$drop1 <- ifelse(tdf$diarrhea_yn==0, "Provider did not assess diarrhea", NA)
tdf$drop2 <- case_when(is.na(tdf$diarrhea_dx) ~ "Not rated",
                        tdf$diarrhea_dx=="Green" ~ "Green",
                        tdf$diarrhea_dx=="Yellow" ~ "Yellow")
tdf$drop2 <- factor(tdf$drop2, levels = c("Green", "Yellow", "Not rated"))
tdf$drop3 <- ifelse(is.na(tdf$rx___12), "Not given", NA)

consort2_ka <- consort_plot(data = tdf,
                            orders = c(screening_id = "Reported diarrhea",
                                       drop1 = "Provider assessment",
                                       screening_id = "Provider assessed diarrhea",
                                       drop2 = "Non-severe IMCI classification",
                                       screening_id = "Rated severe diarrhea",
                                       drop3 = "Treatment status",
                                       screening_id = "Given dehydration treatment"),
                            side_box = c("drop1", "drop2", "drop3"),
                            cex = 0.9)
plot(consort2_ka)
```

```{r}
# Sankey
tdf <- df_ka %>% dplyr::select(cg_report_diarrhea, diarrhea_yn, diarrhea_dx, rx___12)
tdf$cg_report_diarrhea <- ifelse(tdf$cg_report_diarrhea==1, "Diarrhea reported", "Diarrhea not reported")
tdf$cg_report_diarrhea <- factor(tdf$cg_report_diarrhea, levels = c("Diarrhea reported", "Diarrhea not reported"))
tdf$diarrhea_yn <- case_when(tdf$diarrhea_yn==1 ~ "Provider assessed diarrhea",
                             tdf$diarrhea_yn==0 | is.na(tdf$diarrhea_yn) ~ "Provider did not assess diarrhea")
tdf$diarrhea_dx <- ifelse(is.na(tdf$diarrhea_dx), "Not rated", as.character(tdf$diarrhea_dx))
tdf$diarrhea_dx <- factor(tdf$diarrhea_dx, levels = c("Red", "Yellow", "Green", "Not rated"))
tdf$rx___12 <- ifelse(tdf$rx___12==1, "Dehydration treatment given", "No treatment given")
tdf$rx___12 <- factor(tdf$rx___12, levels = c("Dehydration treatment given", "No treatment given"))

s2_ka <- highchart() %>% hc_add_series(data_to_sankey(tdf), "sankey", name = "Diarrhea", hcaes(from = from, to = to, weight = weight),
                      nodes = list(list(id = 'Diarrhea reported'  , color = "#CC6699"),
                                 list(id = 'Diarrhea not reported' , color = "#33CC99"),
                                 list(id = 'Provider assessed diarrhea' , color = "#33CCCC"),
                                 list(id = 'Provider did not assess diarrhea'   , color = "#CC3333"),
                                 list(id = "Red"  , color = "#FF3333"),
                                 list(id = "Yellow"  , color = "#FFFF66"),
                                 list(id = "Green"    , color = "#33CC33"),
                                 list(id = "Not rated"    , color = "darkgrey"),
                                 list(id = "Dehydration treatment given"    , color = "#00FF99"),
                                 list(id = "No treatment given"    , color = "#FF9999")))%>%
                      hc_title(text = "Diarrhea") %>%
                      hc_subtitle(text = "<em/>Care pathway from reported symptoms through treatment</em>") %>%
                      hc_caption(text = "<b/>Data from Kenya</b>") %>%
                      hc_add_theme(plosgph_theme) %>%
                      hc_plotOptions(series = list(dataLabels = list(style = list(fontSize = "11px"))))
s2_ka
```
*I think the order of treatment/no treatment given changed here because there is no Red->Treatment given. The one Red classification did not report diarrhea, so is not included in the consort.*

## Indicator #3 {.tabset}

### Senegal
#### Patient flow through indicator
```{r}
# relevant variables: diarrhea_dx==2 and any_other_red==1 and referral==1 or 2
# Consort
tdf <- df_sn %>% dplyr:::select(screening_id, cg_report_diarrhea, diarrhea_yn, diarrhea_dx, any_other_red, referral2)
tdf <- subset(tdf, cg_report_diarrhea==1)
tdf$drop1 <- ifelse(tdf$diarrhea_yn==0, "Diarrhea not assessed", NA)
tdf$drop2 <- case_when(is.na(tdf$diarrhea_dx) ~ "Not rated",
                        tdf$diarrhea_dx=="Green" ~ "Green",
                        tdf$diarrhea_dx=="Yellow" ~ "Yellow")
tdf$drop2 <- factor(tdf$drop2, levels = c("Green", "Yellow", "Not rated"))
tdf$drop3 <- ifelse(tdf$any_other_red==0, "Not rated red for anything else", NA)
tdf$drop4 <- ifelse(tdf$referral2=="Recorded as not referred", "Not referred", NA)

consort3_sn <- consort_plot(data = tdf,
                            orders = c(screening_id = "Reported diarrhea",
                                       drop1 = "Provider assessment",
                                       screening_id = "Provider assessed diarrhea",
                                       drop2 = "Non-severe IMCI classification",
                                       screening_id = "Rated severe diarrhea",
                                       drop3 = "Other red ratings",
                                       screening_id = "Rated severe on something else",
                                       drop4 = "Referral status",
                                       screening_id = "Referred"),
                            side_box = c("drop1", "drop2", "drop3", "drop4"),
                            cex = 0.9)
plot(consort3_sn)
```

```{r}
# Sankey
tdf <- df_sn %>% dplyr::select(cg_report_diarrhea, diarrhea_yn, diarrhea_dx, any_other_red, referral2)
tdf$cg_report_diarrhea <- ifelse(tdf$cg_report_diarrhea==1, "Diarrhea reported", "Diarrhea not reported")
tdf$cg_report_diarrhea <- factor(tdf$cg_report_diarrhea, levels = c("Diarrhea reported", "Diarrhea not reported"))
tdf$referral2 <- case_when(tdf$referral2=="Urgent" ~ "Referral given",
                           tdf$referral2=="Non-urgent" ~ "Referral given",
                           tdf$referral2=="Recorded as not referred" ~ "No referral given",
                           is.na(tdf$referral2) ~ "Unknown")
tdf$referral2 <- factor(tdf$referral2, levels = c("Referral given", "No referral given", "Unknown"))
tdf$diarrhea_yn <- ifelse(tdf$diarrhea_yn==1, "Provider assessed diarrhea", "Provider did not assesses diarrhea")
tdf$diarrhea_dx <- ifelse(is.na(tdf$diarrhea_dx), "Not rated", as.character(tdf$diarrhea_dx))
tdf$diarrhea_dx <- factor(tdf$diarrhea_dx, levels = c("Red", "Yellow", "Green", "Not rated"))
tdf$any_other_red <- ifelse(tdf$any_other_red==0 | is.na(tdf$any_other_red), "Not rated red for anything else", "Rated red for something else")
tdf$any_other_red <- factor(tdf$any_other_red, levels = c("Rated red for something else", "Not rated red for anything else"))


s3_sn <- highchart() %>% hc_add_series(data_to_sankey(tdf), "sankey", name = "Diarrhea and Other", hcaes(from = from, to = to, weight = weight),
                      nodes = list(list(id = 'Diarrhea reported'  , color = "#CC6699"),
                                 list(id = 'Diarrhea not reported' , color = "#33CC99"),
                                 list(id = 'Provider assessed diarrhea' , color = "#33CCCC"),
                                 list(id = 'Provider did not assess diarrhea'   , color = "#CC3333"),
                                 list(id = "Red"  , color = "#FF3333"),
                                 list(id = "Yellow"  , color = "#FFFF66"),
                                 list(id = "Green"    , color = "#33CC33"),
                                 list(id = "Not rated"    , color = "darkgrey"),
                                 list(id = "Not rated red for anything else"    , color = "#00FF99"),
                                 list(id = "Rated red for something else"    , color = "#FF9999"),
                                 list(id = "Referral given"    , color = "#33CC66"),
                                 list(id = "No referral given"    , color = "#CC6666"),
                                 list(id = "Unknown"    , color = "darkgray")))%>%
                      hc_title(text = "Diarrhea and Other Severe Problems") %>%
                      hc_subtitle(text = "<em/>Care pathway from reported symptoms through referral</em>") %>%
                      hc_caption(text = "<b/>Data from Senegal</b>") %>%
                      hc_add_theme(plosgph_theme) %>%
                      hc_plotOptions(series = list(dataLabels = list(style = list(fontSize = "11px"))))
s3_sn
```


### Tanzania
#### Patient flow through indicator
```{r}
# Consort
tdf <- df_tz %>% dplyr:::select(screening_id, cg_report_diarrhea, diarrhea_yn, diarrhea_dx, any_other_red, referral2)
tdf <- subset(tdf, cg_report_diarrhea==1)
tdf$drop1 <- ifelse(tdf$diarrhea_yn==0, "Diarrhea not assessed", NA)
tdf$drop2 <- case_when(is.na(tdf$diarrhea_dx) ~ "Not rated",
                        tdf$diarrhea_dx=="Green" ~ "Green",
                        tdf$diarrhea_dx=="Yellow" ~ "Yellow")
tdf$drop2 <- factor(tdf$drop2, levels = c("Green", "Yellow", "Not rated"))
tdf$drop3 <- ifelse(tdf$any_other_red==0, "Not rated red for anything else", NA)
tdf$drop4 <- ifelse(tdf$referral2=="Recorded as not referred", "Not referred", NA)

consort3_tz <- consort_plot(data = tdf,
                            orders = c(screening_id = "Reported diarrhea",
                                       drop1 = "Provider assessment",
                                       screening_id = "Provider assessed diarrhea",
                                       drop2 = "Non-severe IMCI classification",
                                       screening_id = "Rated severe diarrhea",
                                       drop3 = "Other red ratings",
                                       screening_id = "Rated severe on something else",
                                       drop4 = "Referral status",
                                       screening_id = "Referred"),
                            side_box = c("drop1", "drop2", "drop3", "drop4"),
                            cex = 0.9)
plot(consort3_tz)
```

```{r}
# Sankey
tdf <- df_tz %>% dplyr::select(cg_report_diarrhea, diarrhea_yn, diarrhea_dx, any_other_red, referral2)
tdf$cg_report_diarrhea <- ifelse(tdf$cg_report_diarrhea==1, "Diarrhea reported", "Diarrhea not reported")
tdf$cg_report_diarrhea <- factor(tdf$cg_report_diarrhea, levels = c("Diarrhea reported", "Diarrhea not reported"))
tdf$referral2 <- case_when(tdf$referral2=="Urgent" ~ "Referral given",
                           tdf$referral2=="Non-urgent" ~ "Referral given",
                           tdf$referral2=="Recorded as not referred" ~ "No referral given",
                           is.na(tdf$referral2) ~ "Unknown")
tdf$referral2 <- factor(tdf$referral2, levels = c("Referral given", "No referral given", "Unknown"))
tdf$diarrhea_yn <- ifelse(tdf$diarrhea_yn==1, "Provider assessed diarrhea", "Provider did not assesses diarrhea")
tdf$diarrhea_dx <- ifelse(is.na(tdf$diarrhea_dx), "Not rated", as.character(tdf$diarrhea_dx))
tdf$diarrhea_dx <- factor(tdf$diarrhea_dx, levels = c("Red", "Yellow", "Green", "Not rated"))
tdf$any_other_red <- ifelse(tdf$any_other_red==0 | is.na(tdf$any_other_red), "Not rated red for anything else", "Rated red for something else")
tdf$any_other_red <- factor(tdf$any_other_red, levels = c("Rated red for something else", "Not rated red for anything else"))


s3_tz <- highchart() %>% hc_add_series(data_to_sankey(tdf), "sankey", name = "Diarrhea and Other", hcaes(from = from, to = to, weight = weight),
                      nodes = list(list(id = 'Diarrhea reported'  , color = "#CC6699"),
                                 list(id = 'Diarrhea not reported' , color = "#33CC99"),
                                 list(id = 'Provider assessed diarrhea' , color = "#33CCCC"),
                                 list(id = 'Provider did not assess diarrhea'   , color = "#CC3333"),
                                 list(id = "Red"  , color = "#FF3333"),
                                 list(id = "Yellow"  , color = "#FFFF66"),
                                 list(id = "Green"    , color = "#33CC33"),
                                 list(id = "Not rated"    , color = "darkgrey"),
                                 list(id = "Not rated red for anything else"    , color = "#00FF99"),
                                 list(id = "Rated red for something else"    , color = "#FF9999"),
                                 list(id = "Referral given"    , color = "#33CC66"),
                                 list(id = "No referral given"    , color = "#CC6666"),
                                 list(id = "Unknown"    , color = "darkgray")))%>%
                      hc_title(text = "Diarrhea and Other Severe Problems") %>%
                      hc_subtitle(text = "<em/>Care pathway from reported symptoms through referral</em>") %>%
                      hc_caption(text = "<b/>Data from Tanzania</b>") %>%
                      hc_add_theme(plosgph_theme) %>%
                      hc_plotOptions(series = list(dataLabels = list(style = list(fontSize = "11px"))))
s3_tz
```

### Kenya
#### Patient flow through indicator
```{r}
# Consort
tdf <- df_ka %>% dplyr:::select(screening_id, cg_report_diarrhea, diarrhea_yn, diarrhea_dx, any_other_red, referral2)
tdf <- subset(tdf, cg_report_diarrhea==1)
tdf$drop1 <- ifelse(tdf$diarrhea_yn==0, "Diarrhea not assessed", NA)
tdf$drop2 <- case_when(is.na(tdf$diarrhea_dx) ~ "Not rated",
                        tdf$diarrhea_dx=="Green" ~ "Green",
                        tdf$diarrhea_dx=="Yellow" ~ "Yellow")
tdf$drop2 <- factor(tdf$drop2, levels = c("Green", "Yellow", "Not rated"))
tdf$drop3 <- ifelse(tdf$any_other_red==0, "Not rated red for anything else", NA)
tdf$drop4 <- ifelse(tdf$referral2=="Recorded as not referred", "Not referred", NA)

consort3_ka <- consort_plot(data = tdf,
                            orders = c(screening_id = "Reported diarrhea",
                                       drop1 = "Provider assessment",
                                       screening_id = "Provider assessed diarrhea",
                                       drop2 = "Non-severe IMCI classification",
                                       screening_id = "Rated severe diarrhea",
                                       drop3 = "Other red ratings",
                                       screening_id = "Rated severe on something else",
                                       drop4 = "Referral status",
                                       screening_id = "Referred"),
                            side_box = c("drop1", "drop2", "drop3", "drop4"),
                            cex = 0.9)
plot(consort3_ka)
```

```{r}
# Sankey
tdf <- df_ka %>% dplyr::select(cg_report_diarrhea, diarrhea_yn, diarrhea_dx, any_other_red, referral2)
tdf$cg_report_diarrhea <- ifelse(tdf$cg_report_diarrhea==1, "Diarrhea reported", "Diarrhea not reported")
tdf$cg_report_diarrhea <- factor(tdf$cg_report_diarrhea, levels = c("Diarrhea reported", "Diarrhea not reported"))
tdf$referral2 <- case_when(tdf$referral2=="Urgent" ~ "Referral given",
                           tdf$referral2=="Non-urgent" ~ "Referral given",
                           tdf$referral2=="Recorded as not referred" ~ "No referral given",
                           is.na(tdf$referral2) ~ "Unknown")
tdf$referral2 <- factor(tdf$referral2, levels = c("Referral given", "No referral given", "Unknown"))
tdf$diarrhea_yn <- ifelse(tdf$diarrhea_yn==0 | is.na(tdf$diarrhea_yn), "Provider did not assess diarrhea", "Provider assessed diarrhea")
tdf$diarrhea_dx <- ifelse(is.na(tdf$diarrhea_dx), "Not rated", as.character(tdf$diarrhea_dx))
tdf$diarrhea_dx <- factor(tdf$diarrhea_dx, levels = c("Red", "Yellow", "Green", "Not rated"))
tdf$any_other_red <- ifelse(tdf$any_other_red==0 | is.na(tdf$any_other_red), "Not rated red for anything else", "Rated red for something else")
tdf$any_other_red <- factor(tdf$any_other_red, levels = c("Rated red for something else", "Not rated red for anything else"))


s3_ka <- highchart() %>% hc_add_series(data_to_sankey(tdf), "sankey", name = "Diarrhea and Other", hcaes(from = from, to = to, weight = weight),
                      nodes = list(list(id = 'Diarrhea reported'  , color = "#CC6699"),
                                 list(id = 'Diarrhea not reported' , color = "#33CC99"),
                                 list(id = 'Provider assessed diarrhea' , color = "#33CCCC"),
                                 list(id = 'Provider did not assess diarrhea'   , color = "#CC3333"),
                                 list(id = "Red"  , color = "#FF3333"),
                                 list(id = "Yellow"  , color = "#FFFF66"),
                                 list(id = "Green"    , color = "#33CC33"),
                                 list(id = "Not rated"    , color = "darkgrey"),
                                 list(id = "Not rated red for anything else"    , color = "#00FF99"),
                                 list(id = "Rated red for something else"    , color = "#FF9999"),
                                 list(id = "Referral given"    , color = "#33CC66"),
                                 list(id = "No referral given"    , color = "#CC6666"),
                                 list(id = "Unknown"    , color = "darkgray")))%>%
                      hc_title(text = "Diarrhea and Other Severe Problems") %>%
                      hc_subtitle(text = "<em/>Care pathway from reported symptoms through referral</em>") %>%
                      hc_caption(text = "<b/>Data from Kenya</b>") %>%
                      hc_add_theme(plosgph_theme) %>%
                      hc_plotOptions(series = list(dataLabels = list(style = list(fontSize = "11px"))))
s3_ka
```

## Indicator #4 {.tabset}

### Senegal
#### Patient flow through indicator
```{r}
# relevant variables: fever_dx==2 and fever_tx==1 and referral==1 or 2
# Consort
tdf <- df_sn %>% dplyr:::select(screening_id, cg_report_fever, fever_yn, fever_dx, fever_tx, referral2)
tdf <- subset(tdf, cg_report_fever==1)
tdf$drop1 <- ifelse(tdf$fever_yn==0, "Fever not assessed", NA)
tdf$drop2 <- case_when(is.na(tdf$fever_dx) ~ "Not rated",
                        tdf$fever_dx=="Green" ~ "Green",
                        tdf$fever_dx=="Yellow" ~ "Yellow")
tdf$drop2 <- factor(tdf$drop2, levels = c("Green", "Yellow", "Not rated"))
tdf$drop3 <- ifelse(tdf$referral2=="Recorded as not referred", "Not referred", NA)
tdf$drop4 <- ifelse(is.na(tdf$fever_tx), "No treatment given", NA)

consort4_sn <- consort_plot(data = tdf,
                            orders = c(screening_id = "Reported fever",
                                       drop1 = "Provider assessment",
                                       screening_id = "Provider assessed fever",
                                       drop2 = "Non-severe IMCI classification",
                                       screening_id = "Rated severe fever",
                                       drop3 = "Referral status",
                                       screening_id = "Referred",
                                       drop4 = "Treatment status",
                                       screening_id = "Given antibiotic or antimalarial"),
                            side_box = c("drop1", "drop2", "drop3", "drop4"),
                            cex = 0.9)
plot(consort4_sn)
```

```{r}
# Sankey
tdf <- df_sn %>% dplyr::select(cg_report_fever, fever_yn, fever_dx, fever_tx, referral2)
tdf$cg_report_fever <- ifelse(tdf$cg_report_fever==1, "Fever reported", "Fever not reported")
tdf$cg_report_fever <- factor(tdf$cg_report_fever, levels = c("Fever reported", "Fever not reported"))
tdf$fever_yn <- ifelse(tdf$fever_yn==1, "Provider assessed fever", "Provider did not assess fever")
tdf$fever_dx <- ifelse(is.na(tdf$fever_dx), "Not rated", as.character(tdf$fever_dx))
tdf$fever_dx <- factor(tdf$fever_dx, levels = c("Red", "Yellow", "Green", "Not rated"))
tdf$fever_tx <- ifelse(tdf$fever_tx==1, "Antibiotic or antimalarial given", "No treatment given")
tdf$fever_tx <- ifelse(is.na(tdf$fever_tx), "No treatment given", tdf$fever_tx)
tdf$referral2 <- case_when(tdf$referral2=="Urgent" ~ "Referral given",
                           tdf$referral2=="Non-urgent" ~ "Referral given",
                           tdf$referral2=="Recorded as not referred" ~ "No referral given",
                           is.na(tdf$referral2) ~ "Unknown")
tdf$referral2 <- factor(tdf$referral2, levels = c("Referral given", "No referral given", "Unknown"))

s4_sn <- highchart() %>% hc_add_series(data_to_sankey(tdf), "sankey", name = "Fever", hcaes(from = from, to = to, weight = weight),
                      nodes = list(list(id = 'Fever reported'  , color = "#CC6699"),
                                 list(id = 'Fever not reported' , color = "#33CC99"),
                                 list(id = 'Provider assessed fever' , color = "#33CCCC"),
                                 list(id = 'Provider did not assess fever'   , color = "#CC3333"),
                                 list(id = "Red"  , color = "#FF3333"),
                                 list(id = "Yellow"  , color = "#FFFF66"),
                                 list(id = "Green"    , color = "#33CC33"),
                                 list(id = "Not rated"    , color = "darkgrey"),
                                 list(id = "Antibiotic or antimalarial given"    , color = "#00FF99"),
                                 list(id = "No treatment given"    , color = "#FF9999"),
                                 list(id = "Referral given"    , color = "#33CC66"),
                                 list(id = "No referral given"    , color = "#CC6666"),
                                 list(id = "Unknown"    , color = "darkgray")))%>%
                      hc_title(text = "Fever") %>%
                      hc_subtitle(text = "<em/>Care pathway from reported symptoms through treatment and referral </em>") %>%
                      hc_caption(text = "<b/>Data from Senegal</b>") %>%
                      hc_add_theme(plosgph_theme) %>%
                      hc_plotOptions(series = list(dataLabels = list(style = list(fontSize = "11px"))))
s4_sn
```

### Tanzania
#### Patient flow through indicator
*Fever treatment and referral switched due to N's.*
```{r}
# Consort
tdf <- df_tz %>% dplyr:::select(screening_id, cg_report_fever, fever_yn, fever_dx, fever_tx, referral2)
tdf <- subset(tdf, cg_report_fever==1)
tdf$drop1 <- ifelse(tdf$fever_yn==0, "Fever not assessed", NA)
tdf$drop2 <- case_when(is.na(tdf$fever_dx) ~ "Not rated",
                        tdf$fever_dx=="Green" ~ "Green",
                        tdf$fever_dx=="Yellow" ~ "Yellow")
tdf$drop2 <- factor(tdf$drop2, levels = c("Green", "Yellow", "Not rated"))
tdf$drop3 <- ifelse(is.na(tdf$fever_tx), "No treatment given", NA)
tdf$drop4 <- ifelse(tdf$referral2=="Recorded as not referred", "Not referred", NA)

consort4_tz <- consort_plot(data = tdf,
                            orders = c(screening_id = "Reported fever",
                                       drop1 = "Provider assessment",
                                       screening_id = "Provider assessed fever",
                                       drop2 = "Non-severe IMCI classification",
                                       screening_id = "Rated severe fever",
                                       drop3 = "Treatment status",
                                       screening_id = "Given antibiotic or antimalarial",
                                       drop4 = "Referral status",
                                       screening_id = "Referred"),
                            side_box = c("drop1", "drop2", "drop3", "drop4"),
                            cex = 0.9)
plot(consort4_tz)
```

```{r}
# Sankey
tdf <- df_tz %>% dplyr::select(cg_report_fever, fever_yn, fever_dx, fever_tx, referral2)
tdf$cg_report_fever <- ifelse(tdf$cg_report_fever==1, "Fever reported", "Fever not reported")
tdf$cg_report_fever <- factor(tdf$cg_report_fever, levels = c("Fever reported", "Fever not reported"))
tdf$fever_yn <- ifelse(tdf$fever_yn==1, "Provider assessed fever", "Provider did not assess fever")
tdf$fever_dx <- ifelse(is.na(tdf$fever_dx), "Not rated", as.character(tdf$fever_dx))
tdf$fever_dx <- factor(tdf$fever_dx, levels = c("Red", "Yellow", "Green", "Not rated"))
tdf$fever_tx <- ifelse(tdf$fever_tx==1, "Antibiotic or antimalarial given", "No treatment given")
tdf$fever_tx <- ifelse(is.na(tdf$fever_tx), "No treatment given", tdf$fever_tx)
tdf$referral2 <- case_when(tdf$referral2=="Urgent" ~ "Referral given",
                           tdf$referral2=="Non-urgent" ~ "Referral given",
                           tdf$referral2=="Recorded as not referred" ~ "No referral given",
                           is.na(tdf$referral2) ~ "Unknown")
tdf$referral2 <- factor(tdf$referral2, levels = c("Referral given", "No referral given", "Unknown"))

s4_tz <- highchart() %>% hc_add_series(data_to_sankey(tdf), "sankey", name = "Fever", hcaes(from = from, to = to, weight = weight),
                      nodes = list(list(id = 'Fever reported'  , color = "#CC6699"),
                                 list(id = 'Fever not reported' , color = "#33CC99"),
                                 list(id = 'Provider assessed fever' , color = "#33CCCC"),
                                 list(id = 'Provider did not assess fever'   , color = "#CC3333"),
                                 list(id = "Red"  , color = "#FF3333"),
                                 list(id = "Yellow"  , color = "#FFFF66"),
                                 list(id = "Green"    , color = "#33CC33"),
                                 list(id = "Not rated"    , color = "darkgrey"),
                                 list(id = "Antibiotic or antimalarial given"    , color = "#00FF99"),
                                 list(id = "No treatment given"    , color = "#FF9999"),
                                 list(id = "Referral given"    , color = "#33CC66"),
                                 list(id = "No referral given"    , color = "#CC6666"),
                                 list(id = "Unknown"    , color = "darkgray")))%>%
                      hc_title(text = "Fever") %>%
                      hc_subtitle(text = "<em/>Care pathway from reported symptoms through treatment and referral </em>") %>%
                      hc_caption(text = "<b/>Data from Tanzania</b>") %>%
                      hc_add_theme(plosgph_theme) %>%
                      hc_plotOptions(series = list(dataLabels = list(style = list(fontSize = "11px"))))
s4_tz
```

### Kenya
#### Patient flow through indicator
```{r}
# Consort
tdf <- df_ka %>% dplyr:::select(screening_id, cg_report_fever, fever_yn, fever_dx, lab_tests___1, fever_tx, referral2)
tdf <- subset(tdf, cg_report_fever==1)
tdf$drop1 <- ifelse(tdf$fever_yn==0, "Fever not assessed", NA)
tdf$drop2 <- case_when(is.na(tdf$fever_dx) ~ "Not rated",
                        tdf$fever_dx=="Green" ~ "Green",
                        tdf$fever_dx=="Yellow" ~ "Yellow")
tdf$drop2 <- factor(tdf$drop2, levels = c("Green", "Yellow", "Not rated"))
tdf$drop3 <- ifelse(is.na(tdf$lab_tests___1), "Not tested for malaria", NA)
tdf$drop4 <- ifelse(is.na(tdf$fever_tx), "No treatment given", NA)
tdf$drop5 <- ifelse(tdf$referral2=="Recorded as not referred", "Not referred", NA)

consort4_ka <- consort_plot(data = tdf,
                            orders = c(screening_id = "Reported fever",
                                       drop1 = "Provider assessment",
                                       screening_id = "Provider assessed fever",
                                       drop2 = "Non-severe IMCI classification",
                                       screening_id = "Rated severe fever",
                                       drop3 = "Malaria test",
                                       screening_id = "Tested for malaria",
                                       drop4 = "Treatment status",
                                       screening_id = "Given antibiotic or antimalarial",
                                       drop5 = "Referral status",
                                       screening_id = "Referred"),
                            side_box = c("drop1", "drop2", "drop3", "drop4", "drop5"),
                            cex = 0.9)
plot(consort4_ka)
```

```{r}
# Sankey
tdf <- df_ka %>% dplyr::select(cg_report_fever, fever_yn, fever_dx, lab_tests___1, fever_tx, referral2)
tdf$cg_report_fever <- ifelse(tdf$cg_report_fever==1, "Fever reported", "Fever not reported")
tdf$cg_report_fever <- factor(tdf$cg_report_fever, levels = c("Fever reported", "Fever not reported"))
tdf$fever_yn <- ifelse(tdf$fever_yn==1, "Provider assessed fever", "Provider did not assess fever")
tdf$fever_dx <- ifelse(is.na(tdf$fever_dx), "Not rated", as.character(tdf$fever_dx))
tdf$fever_dx <- factor(tdf$fever_dx, levels = c("Red", "Yellow", "Green", "Not rated"))
tdf$lab_tests___1 <- ifelse(tdf$lab_tests___1==1, "Tested for malaria", "Not tested for malaria")
tdf$lab_tests___1 <- factor(tdf$lab_tests___1, levels = c("Tested for malaria", "Not tested for malaria"))
tdf$fever_tx <- ifelse(tdf$fever_tx==1, "Antibiotic or antimalarial given", "No treatment given")
tdf$fever_tx <- ifelse(is.na(tdf$fever_tx), "No treatment given", tdf$fever_tx)
tdf$referral2 <- case_when(tdf$referral2=="Urgent" ~ "Referral given",
                           tdf$referral2=="Non-urgent" ~ "Referral given",
                           tdf$referral2=="Recorded as not referred" ~ "No referral given",
                           is.na(tdf$referral2) ~ "Unknown")
tdf$referral2 <- factor(tdf$referral2, levels = c("Referral given", "No referral given", "Unknown"))

s4_ka <- highchart() %>% hc_add_series(data_to_sankey(tdf), "sankey", name = "Fever", hcaes(from = from, to = to, weight = weight),
                      nodes = list(list(id = 'Fever reported'  , color = "#CC6699"),
                                 list(id = 'Fever not reported' , color = "#33CC99"),
                                 list(id = 'Provider assessed fever' , color = "#33CCCC"),
                                 list(id = 'Provider did not assess fever' , color = "#CC3333"),
                                 list(id = "Red"  , color = "#FF3333"),
                                 list(id = "Yellow"  , color = "#FFFF66"),
                                 list(id = "Green"    , color = "#33CC33"),
                                 list(id = "Not rated"    , color = "darkgrey"),
                                 list(id = "Tested for malaria"    , color = "#33CC66"),
                                 list(id = "Not tested for malaria"    , color = "#CC6666"),
                                 list(id = "Antibiotic or antimalarial given"    , color = "#00FF99"),
                                 list(id = "No treatment given"    , color = "#FF9999"),
                                 list(id = "Referral given"    , color = "#33CC66"),
                                 list(id = "No referral given"    , color = "#CC6666"),
                                 list(id = "Unknown"    , color = "darkgray")))%>%
                      hc_title(text = "Fever") %>%
                      hc_subtitle(text = "<em/>Care pathway from reported symptoms through treatment and referral </em>") %>%
                      hc_caption(text = "<b/>Data from Kenya</b>") %>%
                      hc_add_theme(plosgph_theme) %>%
                      hc_plotOptions(series = list(dataLabels = list(style = list(fontSize = "11px"))))
s4_ka
```

# Boxplots of PO measures. {.tabset}

## Senegal
### SpO2
```{r}
boxplot(spo2~age_cat, data=df_sn, main = "Masimo SpO2 Measurement", ylab = "SpO2 (%)", xlab = "Measurement by Age Category")
```

### Pulse Rate
```{r}
boxplot(pr~age_cat, data=df_sn, main = "Masimo PR Measurement", ylab = "PR (beats per minute)", xlab = "Measurement by Age Category")
```

### Respiratory Rate
```{r}
boxplot(rr~age_cat, data=df_sn, main = "Masimo RR Measurement", ylab = "RR (breaths per minute)", xlab = "Measurement by Age Category")
```

### Temperature
```{r}
boxplot(temp_po~age_cat, data=df_sn, main = "Masimo Temperature Measurement", ylab = "Temperature (C)", xlab = "Measurement by Age Category")
```

## Tanzania
### SpO2
```{r}
boxplot(spo2~age_cat, data=df_tz, main = "Masimo SpO2 Measurement", ylab = "SpO2 (%)", xlab = "Measurement by Age Category")
```

### Pulse Rate
```{r}
boxplot(pr~age_cat, data=df_tz, main = "Masimo PR Measurement", ylab = "PR (beats per minute)", xlab = "Measurement by Age Category")
```

### Respiratory Rate
```{r}
boxplot(rr~age_cat, data=df_tz, main = "Masimo RR Measurement", ylab = "RR (breaths per minute)", xlab = "Measurement by Age Category")
```

### Temperature
```{r}
boxplot(temp_po~age_cat, data=df_tz, main = "Masimo Temperature Measurement", ylab = "Temperature (C)", xlab = "Measurement by Age Category")
```

## Kenya
### SpO2
```{r}
boxplot(spo2~age_cat, data=df_ka, main = "Masimo SpO2 Measurement", ylab = "SpO2 (%)", xlab = "Measurement by Age Category")
```

### Pulse Rate
```{r}
boxplot(pr~age_cat, data=df_ka, main = "Masimo PR Measurement", ylab = "PR (beats per minute)", xlab = "Measurement by Age Category")
```

### Respiratory Rate
```{r}
boxplot(rr~age_cat, data=df_ka, main = "Masimo RR Measurement", ylab = "RR (breaths per minute)", xlab = "Measurement by Age Category")
```

### Temperature
```{r}
boxplot(temp_po~age_cat, data=df_ka, main = "Masimo Temperature Measurement", ylab = "Temperature (C)", xlab = "Measurement by Age Category")
```