---
title: "Implementation Study Analysis"
output: html_document
date: "`r Sys.Date()`"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    theme: flatly
---

# Background

The overall goal of this project is to reduce morbidity and mortality of sick children attending primary care facilities while supporting the rational and efficient use of diagnostics and medicines by healthcare providers. This study is focused on understanding the operational feasibility of multimodal pulse ox use in standard care. The results presented in this document describe several weeks of use of the Masimo pulse oximeter in primary care settings.

```{r setup, include=FALSE}
rm(list=ls())

knitr::opts_chunk$set(echo = FALSE)

# install these packages if not already on your computer
library(plyr)
library(dplyr)
library(tableone)
library(kableExtra)

# Read in (cleaned) data
# Create a text file from within R with the name ".Renviron", then define the variables as below
# filename = "<current-file-name>.csv"
# COUNTRY = "<your-country>"
# After adding the file and content restart R session and you are good to go
# The Renviron will be ignored when pushing changes to Github

filename <- Sys.getenv("filename")
df_og <- read.csv(filename)

# Define country and subset
COUNTRY <- Sys.getenv("COUNTRY")
df_og <- subset(df_og, df_og$country==COUNTRY)
```

# Table 1: Patient demographic and household characteristics.
Leila

# Table 2: Patient clinical and care seeking characteristics.
Samwel

# Table 3: Use of PO device across facilities.
```{r}

```


# Table 4: Clinical outcomes following implementation of PO device.
