---
title: "Implementation Study Analysis"
output: html_document
date: "`r Sys.Date()`"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    theme: flatly 
---

# Background

The overall goal of this project is to reduce morbidity and mortality of sick children attending primary care facilities while supporting the rational and efficient use of diagnostics and medicines by healthcare providers. This study is focused on understanding the operational feasibility of multimodal pulse ox use in standard care. The results presented in this document describe several weeks of use of the Masimo pulse oximeter in primary care settings.

```{r setup, include=FALSE}
rm(list=ls())

knitr::opts_chunk$set(echo = FALSE)

# install these packages if not already on your computer
library(plyr)
library(dplyr)
library(tableone)
library(kableExtra)
library(epiDisplay)
library(Hmisc)


# Read in (cleaned) data
# Create a text file from within R with the name ".Renviron", then define the variables as below
# filename = "<current-file-name>.csv"
# COUNTRY = "<your-country>"
# After adding the file and content restart R session and you are good to go
# The Renviron will be ignored when pushing changes to Github

df_og <- read.csv(Sys.getenv("filename"))

# Define country and subset
COUNTRY <- Sys.getenv("COUNTRY")
df <- subset(df_og, df_og$country==COUNTRY)

```

# Table 1: Patient demographic and household characteristics.


```{r}
#CARACTERISTIQUES 

## Sex

df$sex=as.factor(df$sex)
describe(df$sex)
tabpct(df$facility_name,df$sex)

## Relationship of caregiver to child

df$cg_relationship = as.factor(df$cg_relationship)
describe(df$cg_relationship)
tabpct(df$facility_name,df$cg_relationship)

## Maternal education

df$cg_edu_mother=as.factor(df$cg_edu_mother)
describe(df$cg_edu_mother)
tabpct(df$facility_name,df$cg_edu_mother)

## Household head

df$household_head=as.factor(df$household_head)
describe(df$household_head)
tabpct(df$facility_name,df$household_head)

## Household toilet

df$household_toilet=as.factor(df$household_toilet)
describe(df$household_toilet)
tabpct(df$facility_name,df$household_toilet)

## Household fuel

df$household_fuel=as.factor(df$household_fuel)
describe(df$household_fuel)
tabpct(df$facility_name,df$household_fuel)

## Household water located in house

df$household_water_loc=as.factor(df$household_water_loc)
describe(df$household_water_loc)
tabpct(df$facility_name,df$household_water_loc)

## Household floor

df$household_floor=as.factor(df$household_floor)
describe(df$household_floor)
tabpct(df$facility_name,df$household_floor)

```


# Alternative Table One code - Leila

```{r}

# Convert categorical variables into factors

## Sex - omitted since data collected on 'sex' was that of the providers and not the caregiver/child

## Relationship of caregiver to child

df_imp$cg_relationship <- factor(df_imp$cg_relationship,levels = c(1,2,3,4,5,6,7,8,9,10),
                                  labels = c("Mother and Father","Mother and Grandmother","Mother only",
                                             "Father only", "Grandmother only","Grandfather only","Sibling",
                                             "Other family member","Community member", "Other"))


## Maternal education

df_imp$cg_edu_mother<- factor(df_imp$cg_edu_mother,levels = c(1,2,3,4,5,6,7,8,9),
                              labels = c("Primary", "Post-primary/vocational", "Secondary", "Diploma/certificate", "Bachelors degree or equivalent", "Masters degree or equivalent", "Other", "Never attended any formal schooling", "Declined"))


## Household head

df_imp$household_head<- factor(df_imp$household_head,levels = c(1,2,3,4,5,6,7,8,9,10,11,12),
                               labels = c("Female", "Mother of sick child", "Grandmother (maternal)", "Grandmother (paternal)", "Other female", "Male", "Father of sick child", "Grandfather (maternal)", "Grandfather (paternal)", "Other male", "Unknown/uncertain", "Declined"))


## Household toilet

df_imp$household_toilet<- factor(df_imp$household_toilet,levels = c(1,2,3,4,5,6,7,8,9,10,11),
                                 labels = c("Flush or pour-flush toilet", "Ventilated improved pit latrine", "Pit latrine with slab", "Pit latrine without slab/open pit", "Composting toilet", "Bucket", "Hanging toilet", "No facility/bush", "Other", "Unknown/uncertain", "Declined"))


## Household fuel

df_imp$household_fuel<- factor(df_imp$household_fuel,levels = c(1,2,3,4,5,6,7,8,9),
                               labels = c("Firewood", "Charcoal", "Solar", "Biomass fuel", "Cooking gas (LPG fuel)", "Electricity", "Other", "Unknown/uncertain", "Declined"))


## Household water located in house

df_imp$household_water_loc<- factor(df_imp$household_water_loc, levels= c(1,2),
                                    labels = c("In the house/grounds", "Outside the grounds"))


## Household floor

df_imp$household_floor <- factor(df_imp$household_floor, 
                                 levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 
                                                                    11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 
                                                                    99, 999),
                                 labels = c("Natural", "Earth", "Sand", "Clay", "Mud", "Dung", "Rudimentary", "Tablets/Wood planks",
                                            "Palm", "Bamboo", "Mat", "Adobe", "Finished", "Parquet", "Vinyl", "Linoleum", "Ceramic,tile",
                                            "Carpet", "Stone, cement", "Bricks", "Unknown/Uncertain", "Declined"))


# Specify all the variables you want to treat as factors

factorVars <- c("age_cat")

# Specify all the variables to include

myVars <- c("age_cat", "cg_relationship", "cg_age", "cg_edu_mother", "household_head",
            "household_toilet", "household_fuel", "household_water_loc","household_floor")

# CreateTableOne:
out1 <- CreateTableOne(vars = myVars,
                       data = df_imp,
                       factorVars = factorVars,
                       strata = "facility_name",
                       test = FALSE,
                       addOverall = TRUE) 

t1_overall <- print(out1,
            cramVars = c("age_cat", "household_water_loc"))

# Create row labels

t1lab <- c("N", 
          "Age Category = 0-1 month/ 2-59 months",
           "Caregiver Age (mean (SD))", 
           "Maternal Education (highest level attended)", "Primary", "Post-Primary/Vocational", "Secondary", "Diploma/Certificate",
           "Bachelors degree or equivalent", "Masters degree or equivalent", "Other", "Never attended any formal schooling", "Declined",
           "Household head", "Female", "Mother of sick child", "Grandmother (maternal)", "Grandmother (paternal)", "Other female", "Male", "Father of sick child", "Grandfather (maternal)", "Grandfather (paternal)", "Other male", "Unknown/Uncertain", "Declined",
           "What kind of toilet facility do members of your household usually use?", "Flush or pour-flush toilet", "Ventilated improved pit latrine", "Pit latrine with slab", "Pit latrine without slab/open pit", "Composting toilet", "Bucket", "Hanging toilet", "No facility/bush", "Other", "Unknown/Uncertain", "Declined",
           "What type of fuel is mainly used for cooking in the household?", "Firewood","Charcoal", "Solar",  "Biomass fuel", "Cooking gas (LPG fuel)", "Electricity", "Other", "Unknown/Uncertain", "Declined", 
           "Household water location = In the house or grounds/ Outside the grounds",
           "What is the main material of the floor of the household?", "Natural", "Earth", "Sand", "Clay", "Mud", "Dung", "Rudimentary", "Tablets/Wood planks", "Palm", "Bamboo", "Mat", "Adobe", "Finished", "Parquet", "Vinyl", "Linoleum", "Ceramic,tile", "Carpet", "Stone, cement", "Bricks", "Unknown/Uncertain", "Declined")


# Add row labels
rownames(t1_overall) <- c(t1lab)

# Table formatting

t1 <- kable(t1_overall) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center")  %>%
  add_indent(c(5:13, 15:26, 28:38, 40:48, 51:72)) %>%
  pack_rows("Maternal education (highest level attended)", 4, 12) %>%
  pack_rows("Household head", 14, 25) %>%
  pack_rows("What kind of toilet facility do members of your household usually use?", 27, 37) %>%
  pack_rows("What type of fuel is mainly used for cooking in the household?", 39, 47) %>%
  pack_rows("What is the main material of the floor of the household?", 50, 71)

```


# Table 2: Patient clinical and care seeking characteristics.

Samwel

```{r}

## Reason for visit to clinic
df$facility_choice_reason___2 = as.factor(df$facility_choice_reason___2)
describe(df$facility_choice_reason___2)
tabpct(df$facility_name,df$facility_choice_reason___2)

df$facility_choice_reason___3 = as.factor(df$facility_choice_reason___3)
describe(df$facility_choice_reason___3)
tabpct(df$facility_name,df$facility_choice_reason___3)

df$facility_choice_reason___4 = as.factor(df$facility_choice_reason___4)
describe(df$facility_choice_reason___4)
tabpct(df$facility_name,df$facility_choice_reason___4)

df$facility_choice_reason___5 = as.factor(df$facility_choice_reason___5)
describe(df$facility_choice_reason___5)
tabpct(df$facility_name,df$facility_choice_reason___5)

df$facility_choice_reason___8 = as.factor(df$facility_choice_reason___8)
describe(df$facility_choice_reason___8)
tabpct(df$facility_name,df$facility_choice_reason___8)

## ## Mode of travel to clinic

df$travel_mode___1=as.factor(df$travel_mode___1) 
describe(df$travel_mode___1)
tabpct(df$facility_name,df$travel_mode___1)

df$travel_mode___2=as.factor(df$travel_mode___2)
describe(df$travel_mode___2)

df$travel_mode___3=as.factor(df$travel_mode___3)
describe(df$travel_mode___3)
tabpct(df$facility_name,df$travel_mode___3)

df$travel_mode___4=as.factor(df$travel_mode___4)
describe(df$travel_mode___4)

df$travel_mode___5=as.factor(df$travel_mode___5) 
describe(df$travel_mode___5)

df$travel_mode___6=as.factor(df$travel_mode___6)
describe(df$travel_mode___6)
tabpct(df$facility_name,df$travel_mode___6)

df$travel_mode___7=as.factor(df$travel_mode___7)
describe(df$travel_mode___7)
tabpct(df$facility_name,df$travel_mode___7)

df$travel_mode___8=as.factor(df$travel_mode___8)
describe(df$travel_mode___8)
tabpct(df$facility_name,df$travel_mode___8)

if( COUNTRY != "Tanzania") {
  df$travel_mode___9=as.factor(df$travel_mode___9)
  describe(df$travel_mode___9)
  tabpct(df$facility_name,df$travel_mode___9)
  
  df$travel_mode___10=as.factor(df$travel_mode___10)
  describe(df$travel_mode___10)
  tabpct(df$facility_name,df$travel_mode___10)
  
  df$travel_mode___999=as.factor(df$travel_mode___999)
  describe(df$travel_mode___999)
  tabpct(df$facility_name,df$travel_mode___999)
}
df$travel_mode___11=as.factor(df$travel_mode___11)
describe(df$travel_mode___11)
tabpct(df$facility_name,df$travel_mode___11)



## Travel time to arrive at clinic

df$travel_time=as.factor(df$travel_time)
describe(df$travel_time)
tabpct(df$facility_name,df$travel_time)

## Estimated amount of money spent for transport to arrive at clinic (USD)

df$travel_cost=as.factor(df$travel_cost)
describe(df$travel_cost)
tabpct(df$facility_name,df$travel_cost)
```

======= \## Age Category

IS$visit_date=as.Date(IS$visit_date) IS$Birthday=as.Date(IS$Birthday)

IS$Age_categ = difftime(IS$visit_date,IS$Birthday,units = "days") IS$age_categorie = IS$Age_categ/30 print(IS$age_categorie) IS$age_categorie=as.numeric(IS$age_categorie) summ(IS\$age_categorie)

IS$age_categorie_1 = cut(IS$age_categorie, breaks = c(0,2,12,60,100), right = F, labels = c("0-1","2-11","12-59","60-66")) describe(IS$age_categorie_1) tabpct(IS$facility_name,IS\$age_categorie_1)

## Sex

IS$sex=as.factor(IS$sex) describe(IS$sex) tabpct(IS$facility_name,IS\$sex)

## Relationship of caregiver to child

IS$cg_relationship = as.factor(IS$cg_relationship) describe(IS$cg_relationship) tabpct(IS$facility_name,IS\$cg_relationship)

## Maternal education

IS$cg_edu_mother=as.factor(IS$cg_edu_mother) describe(IS$cg_edu_mother) tabpct(IS$facility_name,IS\$cg_edu_mother)

## Household head

IS$household_head=as.factor(IS$household_head) describe(IS$household_head) tabpct(IS$facility_name,IS\$household_head)

## Household toilet

IS$household_toilet=as.factor(IS$household_toilet) describe(IS$household_toilet) tabpct(IS$facility_name,IS\$household_toilet)

## Household fuel

IS$household_fuel=as.factor(IS$household_fuel) describe(IS$household_fuel) tabpct(IS$facility_name,IS\$household_fuel)

## Household water located in house

IS$household_water_loc=as.factor(IS$household_water_loc) describe(IS$household_water_loc) tabpct(IS$facility_name,IS\$household_water_loc)

## Household floor

IS$household_floor=as.factor(IS$household_floor) describe(IS$household_floor) tabpct(IS$facility_name,IS\$household_floor)

# Table 2: Patient clinical and care seeking characteristics.

```{r}

## Reason for visit to clinic
IS$facility_choice_reason___2 = as.factor(IS$facility_choice_reason___2)
describe(IS$facility_choice_reason___2)
tabpct(IS$facility_name,IS$facility_choice_reason___2)

IS$facility_choice_reason___3 = as.factor(IS$facility_choice_reason___3)
describe(IS$facility_choice_reason___3)
tabpct(IS$facility_name,IS$facility_choice_reason___3)

IS$facility_choice_reason___4 = as.factor(IS$facility_choice_reason___4)
describe(IS$facility_choice_reason___4)
tabpct(IS$facility_name,IS$facility_choice_reason___4)

IS$facility_choice_reason___5 = as.factor(IS$facility_choice_reason___5)
describe(IS$facility_choice_reason___5)
tabpct(IS$facility_name,IS$facility_choice_reason___5)

IS$facility_choice_reason___8 = as.factor(IS$facility_choice_reason___8)
describe(IS$facility_choice_reason___8)
tabpct(IS$facility_name,IS$facility_choice_reason___8)

## ## Mode of travel to clinic

IS$travel_mode___1=as.factor(IS$travel_mode___1)
describe(IS$travel_mode___1)
tabpct(IS$facility_name,IS$travel_mode___1)

IS$travel_mode___2=as.factor(IS$travel_mode___2)
describe(IS$travel_mode___2)

IS$travel_mode___3=as.factor(IS$travel_mode___3)
describe(IS$travel_mode___3)
tabpct(IS$facility_name,IS$travel_mode___3)

IS$travel_mode___4=as.factor(IS$travel_mode___4)
describe(IS$travel_mode___4)

IS$travel_mode___5=as.factor(IS$travel_mode___5)
describe(IS$travel_mode___5)

IS$travel_mode___6=as.factor(IS$travel_mode___6)
describe(IS$travel_mode___6)
tabpct(IS$facility_name,IS$travel_mode___6)

IS$travel_mode___7=as.factor(IS$travel_mode___7)
describe(IS$travel_mode___7)
tabpct(IS$facility_name,IS$travel_mode___7)

IS$travel_mode___8=as.factor(IS$travel_mode___8)
describe(IS$travel_mode___8)
tabpct(IS$facility_name,IS$travel_mode___8)

IS$travel_mode___9=as.factor(IS$travel_mode___9)
describe(IS$travel_mode___9)
tabpct(IS$facility_name,IS$travel_mode___9)

IS$travel_mode___10=as.factor(IS$travel_mode___10)
describe(IS$travel_mode___10)
tabpct(IS$facility_name,IS$travel_mode___10)

IS$travel_mode___11=as.factor(IS$travel_mode___11)
describe(IS$travel_mode___11)
tabpct(IS$facility_name,IS$travel_mode___11)

IS$travel_mode___999=as.factor(IS$travel_mode___999)
describe(IS$travel_mode___999)
tabpct(IS$facility_name,IS$travel_mode___999)

## Travel time to arrive at clinic

IS$travel_time=as.factor(IS$travel_time)
describe(IS$travel_time)
tabpct(IS$facility_name,IS$travel_time)

## Estimated amount of money spent for transport to arrive at clinic (USD)

IS$travel_cost=as.factor(IS$travel_cost)
describe(IS$travel_cost)
tabpct(IS$facility_name,IS$travel_cost)
```

# Table 3: Use of PO device across facilities.

```{r}

## PO device used during encounter

df$used_po_yn=as.factor(df$used_po_yn)
describe(df$used_po_yn)

## PO device used correctly

df$correct_use_yn=as.factor(df$correct_use_yn)
describe(df$correct_use_yn)
tabpct(df$facility_name,df$correct_use_yn)

## Duration of PO device use

df$duration_po =difftime(df$po_stop,df$po_start, units = "mins")
print(df$duration_po)
df$duration_po=as.numeric(df$duration_po)
summ(df$duration_po)
df$duration_po_1 = cut(df$duration_po,
                       breaks = c(0,1,3.1,5.1,10.1,30.1,60),
                       right = F,
                       labels = c("Moins une min","1 à 3 m","4-5m","6-10m","11-30","31-60"))
describe(df$duration_po_1)
tabpct(df$facility_name,df$duration_po_1)

## Consultation duration
df$consult_start=as.POSIXlt(df$consult_start, format = "%H:%M")
df$consult_stop=as.POSIXct(df$consult_stop, format = "%H:%M")
df$consultation_duration = difftime(df$consult_stop,df$consult_start,units = "mins")
print(df$consultation_duration)
df$consultation_duration=as.numeric(df$consultation_duration)
summ(df$consultation_duration)
df$consultation_duration_1 = cut(df$consultation_duration,
                       breaks = c(0,2.1,5.1,10.1,30.1,60.1,100),
                       right = F,
                       labels = c("2 min","3-5m","6-10m","11-30","31-60","Plus 60"))
describe(df$consultation_duration_1)
tabpct(df$facility_name,df$consultation_duration_1)

## Encounters where all clinical measurements were assessed

df$correct_use_measurements = df$correct_use_measurements___1 + df$correct_use_measurements___2 +
  df$correct_use_measurements___3 + df$correct_use_measurements___4
df$correct_use_measurements=as.factor(df$correct_use_measurements)
describe(df$correct_use_measurements)
tabpct(df$facility_name,df$correct_use_measurements)

df$used_po_yn=as.factor(df$used_po_yn)
describe(df$used_po_yn)

## PO device used correctly

df$correct_use_yn=as.factor(df$correct_use_yn)
describe(df$correct_use_yn)
tabpct(df$facility_name,df$correct_use_yn)

## Duration of PO device use

df$duration_po =difftime(df$po_stop,df$po_start, units = "mins")
print(df$duration_po)
df$duration_po=as.numeric(df$duration_po)
summ(df$duration_po)
df$duration_po_1 = cut(df$duration_po,
                       breaks = c(0,1,3.1,5.1,10.1,30.1,60),
                       right = F,
                       labels = c("Moins une min","1 à 3 m","4-5m","6-10m","11-30","31-60"))
describe(df$duration_po_1)
tabpct(df$facility_name,df$duration_po_1)

## Consultation duration

df$consultation_duration = difftime(df$consult_stop,df$consult_start,units = "mins")
print(df$consultation_duration)
df$consultation_duration=as.numeric(df$consultation_duration)
summ(df$consultation_duration)
df$consultation_duration_1 = cut(df$consultation_duration,
                       breaks = c(0,2.1,5.1,10.1,30.1,60.1,100),
                       right = F,
                       labels = c("2 min","3-5m","6-10m","11-30","31-60","Plus 60"))
describe(df$consultation_duration_1)
tabpct(df$facility_name,df$consultation_duration_1)

## Encounters where all clinical measurements were assessed

df$correct_use_measurements = df$correct_use_measurements___1 + df$correct_use_measurements___2 +
  df$correct_use_measurements___3 + df$correct_use_measurements___4
df$correct_use_measurements=as.factor(df$correct_use_measurements)
describe(df$correct_use_measurements)
tabpct(df$facility_name,df$correct_use_measurements)
```

```{r}
# Specify all the variables you want to treat as factors

factorVars <- c("used_po_yn", "correct_use_yn", "clinical_measures_complete")

# Specify all the variables to include in table (both continuous and categorical)
myVars <- c("used_po_yn", "correct_use_yn", "po_duration_min", "consult_duration_min", "clinical_measures_complete")

## issue identified w/duration variables, troubleshooting in progress in cleaning file

t3lab <- c("N", "Used PO device during encounter (%)", "PO device used correctly (%)", "Duration of PO device use, minutes (mean (SD))", "Consult duration, minutes (mean (SD))", "All clinical measures (SpO2, PR, RR, Temp) collected (%)")

out3 <- CreateTableOne(vars = myVars,
               data = df,
               factorVars = factorVars,
               strata = "facility_name",
               test = FALSE,
               addOverall = TRUE)
out3_overall <- print(out3)
rownames(out3_overall) <- c(t3lab) # Add row labels

out3 <- kable(print(out3_overall)) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"), position = "center")
```
`r out3`

The PO device was used consistently across encounters except for:
* `r sum(df_og$no_po_reason==1, na.rm = T)` instances where the device was broken
* `r sum(df_og$no_po_reason==2, na.rm = T)` instances where the battery was not charged
* `r sum(df_og$no_po_reason==3, na.rm = T)` instances where the device was being used in another part of the facility
* `r sum(df_og$no_po_reason==4, na.rm = T)` instances where the device was missing
* `r sum(df_og$no_po_reason==5, na.rm = T)` instances where the child was too fussy
* `r sum(df_og$no_po_reason==6, na.rm = T)` instances where the caregiver did not want it
* `r sum(df_og$no_po_reason==7, na.rm = T)` instances where the provider decided it was not needed

# Table 4: Clinical outcomes following implementation of PO device.
