---
title: "Implementation Study Analysis"
output: html_document
date: "`r Sys.Date()`"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    theme: flatly 
---

# Background

The overall goal of this project is to reduce morbidity and mortality of sick children attending primary care facilities while supporting the rational and efficient use of diagnostics and medicines by healthcare providers. This study is focused on understanding the operational feasibility of multimodal pulse ox use in standard care. The results presented in this document describe several weeks of use of the Masimo pulse oximeter in primary care settings.

```{r setup, include=FALSE}
rm(list=ls())

knitr::opts_chunk$set(echo = FALSE)

# install these packages if not already on your computer
library(plyr)
library(dplyr)
library(tableone)
library(kableExtra)
library(epiDisplay)
library(Hmisc)


# Read in (cleaned) data
# Create a text file from within R with the name ".Renviron", then define the variables as below
# filename = "<current-file-name>.csv"
# COUNTRY = "<your-country>"
# After adding the file and content restart R session and you are good to go
# The Renviron will be ignored when pushing changes to Github

df_og <- read.csv(Sys.getenv("filename"))

# Define country and subset
COUNTRY <- Sys.getenv("COUNTRY")
df_sn <- subset(df_og, df_og$country==COUNTRY)

```

# Table 1: Patient demographic and household characteristics.

Leila

```{r}
#CARACTERISTIQUES 

## Sex

df_sn$sex=as.factor(df_sn$sex)
describe(df_sn$sex)
tabpct(df_sn$facility_name,df_sn$sex)

## Relationship of caregiver to child

df_sn$cg_relationship = as.factor(df_sn$cg_relationship)
describe(df_sn$cg_relationship)
tabpct(df_sn$facility_name,df_sn$cg_relationship)

## Maternal education

df_sn$cg_edu_mother=as.factor(df_sn$cg_edu_mother)
describe(df_sn$cg_edu_mother)
tabpct(df_sn$facility_name,df_sn$cg_edu_mother)

## Household head

df_sn$household_head=as.factor(df_sn$household_head)
describe(df_sn$household_head)
tabpct(df_sn$facility_name,df_sn$household_head)

## Household toilet

df_sn$household_toilet=as.factor(df_sn$household_toilet)
describe(df_sn$household_toilet)
tabpct(df_sn$facility_name,df_sn$household_toilet)

## Household fuel

df_sn$household_fuel=as.factor(df_sn$household_fuel)
describe(df_sn$household_fuel)
tabpct(df_sn$facility_name,df_sn$household_fuel)

## Household water located in house

df_sn$household_water_loc=as.factor(df_sn$household_water_loc)
describe(df_sn$household_water_loc)
tabpct(df_sn$facility_name,df_sn$household_water_loc)

## Household floor

df_sn$household_floor=as.factor(df_sn$household_floor)
describe(df_sn$household_floor)
tabpct(df_sn$facility_name,df_sn$household_floor)

```

# Table 2: Patient clinical and care seeking characteristics.

Samwel

```{r}

## Reason for visit to clinic
df_sn$facility_choice_reason___2 = as.factor(df_sn$facility_choice_reason___2)
describe(df_sn$facility_choice_reason___2)
tabpct(df_sn$facility_name,df_sn$facility_choice_reason___2)

df_sn$facility_choice_reason___3 = as.factor(df_sn$facility_choice_reason___3)
describe(df_sn$facility_choice_reason___3)
tabpct(df_sn$facility_name,df_sn$facility_choice_reason___3)

df_sn$facility_choice_reason___4 = as.factor(df_sn$facility_choice_reason___4)
describe(df_sn$facility_choice_reason___4)
tabpct(df_sn$facility_name,df_sn$facility_choice_reason___4)

df_sn$facility_choice_reason___5 = as.factor(df_sn$facility_choice_reason___5)
describe(df_sn$facility_choice_reason___5)
tabpct(df_sn$facility_name,df_sn$facility_choice_reason___5)

df_sn$facility_choice_reason___8 = as.factor(df_sn$facility_choice_reason___8)
describe(df_sn$facility_choice_reason___8)
tabpct(df_sn$facility_name,df_sn$facility_choice_reason___8)

## ## Mode of travel to clinic

df_sn$travel_mode___1=as.factor(df_sn$travel_mode___1) 
describe(df_sn$travel_mode___1)
tabpct(df_sn$facility_name,df_sn$travel_mode___1)

df_sn$travel_mode___2=as.factor(df_sn$travel_mode___2)
describe(df_sn$travel_mode___2)

df_sn$travel_mode___3=as.factor(df_sn$travel_mode___3)
describe(df_sn$travel_mode___3)
tabpct(df_sn$facility_name,df_sn$travel_mode___3)

df_sn$travel_mode___4=as.factor(df_sn$travel_mode___4)
describe(df_sn$travel_mode___4)

df_sn$travel_mode___5=as.factor(df_sn$travel_mode___5) 
describe(df_sn$travel_mode___5)

df_sn$travel_mode___6=as.factor(df_sn$travel_mode___6)
describe(df_sn$travel_mode___6)
tabpct(df_sn$facility_name,df_sn$travel_mode___6)

df_sn$travel_mode___7=as.factor(df_sn$travel_mode___7)
describe(df_sn$travel_mode___7)
tabpct(df_sn$facility_name,df_sn$travel_mode___7)

df_sn$travel_mode___8=as.factor(df_sn$travel_mode___8)
describe(df_sn$travel_mode___8)
tabpct(df_sn$facility_name,df_sn$travel_mode___8)

if( COUNTRY != "Tanzania") {
  df_sn$travel_mode___9=as.factor(df_sn$travel_mode___9)
  describe(df_sn$travel_mode___9)
  tabpct(df_sn$facility_name,df_sn$travel_mode___9)
  
  df_sn$travel_mode___10=as.factor(df_sn$travel_mode___10)
  describe(df_sn$travel_mode___10)
  tabpct(df_sn$facility_name,df_sn$travel_mode___10)
  
  df_sn$travel_mode___999=as.factor(df_sn$travel_mode___999)
  describe(df_sn$travel_mode___999)
  tabpct(df_sn$facility_name,df_sn$travel_mode___999)
}
df_sn$travel_mode___11=as.factor(df_sn$travel_mode___11)
describe(df_sn$travel_mode___11)
tabpct(df_sn$facility_name,df_sn$travel_mode___11)



## Travel time to arrive at clinic

df_sn$travel_time=as.factor(df_sn$travel_time)
describe(df_sn$travel_time)
tabpct(df_sn$facility_name,df_sn$travel_time)

## Estimated amount of money spent for transport to arrive at clinic (USD)

df_sn$travel_cost=as.factor(df_sn$travel_cost)
describe(df_sn$travel_cost)
tabpct(df_sn$facility_name,df_sn$travel_cost)
```

======= \## Age Category

IS$visit_date=as.Date(IS$visit_date) IS$Birthday=as.Date(IS$Birthday)

IS$Age_categ = difftime(IS$visit_date,IS$Birthday,units = "days") IS$age_categorie = IS$Age_categ/30 print(IS$age_categorie) IS$age_categorie=as.numeric(IS$age_categorie) summ(IS\$age_categorie)

IS$age_categorie_1 = cut(IS$age_categorie, breaks = c(0,2,12,60,100), right = F, labels = c("0-1","2-11","12-59","60-66")) describe(IS$age_categorie_1) tabpct(IS$facility_name,IS\$age_categorie_1)

## Sex

IS$sex=as.factor(IS$sex) describe(IS$sex) tabpct(IS$facility_name,IS\$sex)

## Relationship of caregiver to child

IS$cg_relationship = as.factor(IS$cg_relationship) describe(IS$cg_relationship) tabpct(IS$facility_name,IS\$cg_relationship)

## Maternal education

IS$cg_edu_mother=as.factor(IS$cg_edu_mother) describe(IS$cg_edu_mother) tabpct(IS$facility_name,IS\$cg_edu_mother)

## Household head

IS$household_head=as.factor(IS$household_head) describe(IS$household_head) tabpct(IS$facility_name,IS\$household_head)

## Household toilet

IS$household_toilet=as.factor(IS$household_toilet) describe(IS$household_toilet) tabpct(IS$facility_name,IS\$household_toilet)

## Household fuel

IS$household_fuel=as.factor(IS$household_fuel) describe(IS$household_fuel) tabpct(IS$facility_name,IS\$household_fuel)

## Household water located in house

IS$household_water_loc=as.factor(IS$household_water_loc) describe(IS$household_water_loc) tabpct(IS$facility_name,IS\$household_water_loc)

## Household floor

IS$household_floor=as.factor(IS$household_floor) describe(IS$household_floor) tabpct(IS$facility_name,IS\$household_floor)

# Table 2: Patient clinical and care seeking characteristics.

```{r}

## Reason for visit to clinic
IS$facility_choice_reason___2 = as.factor(IS$facility_choice_reason___2)
describe(IS$facility_choice_reason___2)
tabpct(IS$facility_name,IS$facility_choice_reason___2)

IS$facility_choice_reason___3 = as.factor(IS$facility_choice_reason___3)
describe(IS$facility_choice_reason___3)
tabpct(IS$facility_name,IS$facility_choice_reason___3)

IS$facility_choice_reason___4 = as.factor(IS$facility_choice_reason___4)
describe(IS$facility_choice_reason___4)
tabpct(IS$facility_name,IS$facility_choice_reason___4)

IS$facility_choice_reason___5 = as.factor(IS$facility_choice_reason___5)
describe(IS$facility_choice_reason___5)
tabpct(IS$facility_name,IS$facility_choice_reason___5)

IS$facility_choice_reason___8 = as.factor(IS$facility_choice_reason___8)
describe(IS$facility_choice_reason___8)
tabpct(IS$facility_name,IS$facility_choice_reason___8)

## ## Mode of travel to clinic

IS$travel_mode___1=as.factor(IS$travel_mode___1)
describe(IS$travel_mode___1)
tabpct(IS$facility_name,IS$travel_mode___1)

IS$travel_mode___2=as.factor(IS$travel_mode___2)
describe(IS$travel_mode___2)

IS$travel_mode___3=as.factor(IS$travel_mode___3)
describe(IS$travel_mode___3)
tabpct(IS$facility_name,IS$travel_mode___3)

IS$travel_mode___4=as.factor(IS$travel_mode___4)
describe(IS$travel_mode___4)

IS$travel_mode___5=as.factor(IS$travel_mode___5)
describe(IS$travel_mode___5)

IS$travel_mode___6=as.factor(IS$travel_mode___6)
describe(IS$travel_mode___6)
tabpct(IS$facility_name,IS$travel_mode___6)

IS$travel_mode___7=as.factor(IS$travel_mode___7)
describe(IS$travel_mode___7)
tabpct(IS$facility_name,IS$travel_mode___7)

IS$travel_mode___8=as.factor(IS$travel_mode___8)
describe(IS$travel_mode___8)
tabpct(IS$facility_name,IS$travel_mode___8)

IS$travel_mode___9=as.factor(IS$travel_mode___9)
describe(IS$travel_mode___9)
tabpct(IS$facility_name,IS$travel_mode___9)

IS$travel_mode___10=as.factor(IS$travel_mode___10)
describe(IS$travel_mode___10)
tabpct(IS$facility_name,IS$travel_mode___10)

IS$travel_mode___11=as.factor(IS$travel_mode___11)
describe(IS$travel_mode___11)
tabpct(IS$facility_name,IS$travel_mode___11)

IS$travel_mode___999=as.factor(IS$travel_mode___999)
describe(IS$travel_mode___999)
tabpct(IS$facility_name,IS$travel_mode___999)

## Travel time to arrive at clinic

IS$travel_time=as.factor(IS$travel_time)
describe(IS$travel_time)
tabpct(IS$facility_name,IS$travel_time)

## Estimated amount of money spent for transport to arrive at clinic (USD)

IS$travel_cost=as.factor(IS$travel_cost)
describe(IS$travel_cost)
tabpct(IS$facility_name,IS$travel_cost)
```

# Table 3: Use of PO device across facilities.

```{r}

## PO device used during encounter

df_sn$used_po_yn=as.factor(df_sn$used_po_yn)
describe(df_sn$used_po_yn)

## PO device used correctly

df_sn$correct_use_yn=as.factor(df_sn$correct_use_yn)
describe(df_sn$correct_use_yn)
tabpct(df_sn$facility_name,df_sn$correct_use_yn)

## Duration of PO device use

df_sn$duration_po =difftime(df_sn$po_stop,df_sn$po_start, units = "mins")
print(df_sn$duration_po)
df_sn$duration_po=as.numeric(df_sn$duration_po)
summ(df_sn$duration_po)
df_sn$duration_po_1 = cut(df_sn$duration_po,
                       breaks = c(0,1,3.1,5.1,10.1,30.1,60),
                       right = F,
                       labels = c("Moins une min","1 à 3 m","4-5m","6-10m","11-30","31-60"))
describe(df_sn$duration_po_1)
tabpct(df_sn$facility_name,df_sn$duration_po_1)

## Consultation duration
df_sn$consult_start=as.POSIXlt(df_sn$consult_start, format = "%H:%M")
df_sn$consult_stop=as.POSIXct(df_sn$consult_stop, format = "%H:%M")
df_sn$consultation_duration = difftime(df_sn$consult_stop,df_sn$consult_start,units = "mins")
print(df_sn$consultation_duration)
df_sn$consultation_duration=as.numeric(df_sn$consultation_duration)
summ(df_sn$consultation_duration)
df_sn$consultation_duration_1 = cut(df_sn$consultation_duration,
                       breaks = c(0,2.1,5.1,10.1,30.1,60.1,100),
                       right = F,
                       labels = c("2 min","3-5m","6-10m","11-30","31-60","Plus 60"))
describe(df_sn$consultation_duration_1)
tabpct(df_sn$facility_name,df_sn$consultation_duration_1)

## Encounters where all clinical measurements were assessed

df_sn$correct_use_measurements = df_sn$correct_use_measurements___1 + df_sn$correct_use_measurements___2 +
  df_sn$correct_use_measurements___3 + df_sn$correct_use_measurements___4
df_sn$correct_use_measurements=as.factor(df_sn$correct_use_measurements)
describe(df_sn$correct_use_measurements)
tabpct(df_sn$facility_name,df_sn$correct_use_measurements)

IS$used_po_yn=as.factor(IS$used_po_yn)
describe(IS$used_po_yn)

## PO device used correctly

IS$correct_use_yn=as.factor(IS$correct_use_yn)
describe(IS$correct_use_yn)
tabpct(IS$facility_name,IS$correct_use_yn)

## Duration of PO device use

IS$duration_po =difftime(IS$po_stop,IS$po_start, units = "mins")
print(IS$duration_po)
IS$duration_po=as.numeric(IS$duration_po)
summ(IS$duration_po)
IS$duration_po_1 = cut(IS$duration_po,
                       breaks = c(0,1,3.1,5.1,10.1,30.1,60),
                       right = F,
                       labels = c("Moins une min","1 à 3 m","4-5m","6-10m","11-30","31-60"))
describe(IS$duration_po_1)
tabpct(IS$facility_name,IS$duration_po_1)

## Consultation duration

IS$consultation_duration = difftime(IS$consult_stop,IS$consult_start,units = "mins")
print(IS$consultation_duration)
IS$consultation_duration=as.numeric(IS$consultation_duration)
summ(IS$consultation_duration)
IS$consultation_duration_1 = cut(IS$consultation_duration,
                       breaks = c(0,2.1,5.1,10.1,30.1,60.1,100),
                       right = F,
                       labels = c("2 min","3-5m","6-10m","11-30","31-60","Plus 60"))
describe(IS$consultation_duration_1)
tabpct(IS$facility_name,IS$consultation_duration_1)

## Encounters where all clinical measurements were assessed

IS$correct_use_measurements = IS$correct_use_measurements___1 + IS$correct_use_measurements___2 +
  IS$correct_use_measurements___3 + IS$correct_use_measurements___4
IS$correct_use_measurements=as.factor(IS$correct_use_measurements)
describe(IS$correct_use_measurements)
tabpct(IS$facility_name,IS$correct_use_measurements)


```

# Table 4: Clinical outcomes following implementation of PO device.
